---
title: "Example Data Generation"
date: "`r Sys.Date()`"
output:
    rmarkdown::html_document:
        theme: "spacelab"
        highlight: "kate"
        toc: true
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Example Data Generation}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
editor_options:
    markdown: 
        wrap: 72
---

## Generating minimal data to test `teal.modules.clinical`

The following script is used to create and save cached synthetic CDISC data to the `data/` directory to use in examples and tests in the `teal.modules.clinical` package. This script/vignette was initialized by Emily de la Rua in `tern`.

_Disclaimer_: this vignette concerns mainly the development of minimal and stable test data and it is kept internal for feature traceability.

## Setup & Helper Functions

```{r setup, eval=FALSE}
library(dplyr)
library(formatters)

study_duration_secs <- 31556952 * 2

sample_fct <- function(x, N, ...) { # nolint
  checkmate::assert_number(N)
  factor(sample(x, N, replace = TRUE, ...), levels = if (is.factor(x)) levels(x) else x)
}

retain <- function(df, value_var, event, outside = NA) {
  indices <- c(1, which(event == TRUE), nrow(df) + 1)
  values <- c(outside, value_var[event == TRUE])
  rep(values, diff(indices))
}

relvar_init <- function(relvar1, relvar2) {
  if (length(relvar1) != length(relvar2)) {
    message(simpleError(
      "The argument value length of relvar1 and relvar2 differ. They must contain the same number of elements."
    ))
    return(NA)
  }
  return(list("relvar1" = relvar1, "relvar2" = relvar2))
}

rel_var <- function(df = NULL, var_name = NULL, var_values = NULL, related_var = NULL) {
  if (is.null(df)) {
    message("Missing data frame argument value.")
    return(NA)
  } else {
    n_relvar1 <- length(unique(df[, related_var, drop = TRUE]))
    n_relvar2 <- length(var_values)
    if (n_relvar1 != n_relvar2) {
      message(paste("Unequal vector lengths for", related_var, "and", var_name))
      return(NA)
    } else {
      relvar1 <- unique(df[, related_var, drop = TRUE])
      relvar2_values <- rep(NA, nrow(df))
      for (r in seq_len(length(relvar1))) {
        matched <- which(df[, related_var, drop = TRUE] == relvar1[r])
        relvar2_values[matched] <- var_values[r]
      }
      return(relvar2_values)
    }
  }
}

visit_schedule <- function(visit_format = "WEEK",
                           n_assessments = 10L,
                           n_days = 5L) {
  if (!(toupper(visit_format) %in% c("WEEK", "CYCLE"))) {
    message("Visit format value must either be: WEEK or CYCLE")
    return(NA)
  }
  if (toupper(visit_format) == "WEEK") {
    assessments <- 1:n_assessments
    assessments_ord <- -1:n_assessments
    visit_values <- c("SCREENING", "BASELINE", paste(toupper(visit_format), assessments, "DAY", (assessments * 7) + 1))
  } else if (toupper(visit_format) == "CYCLE") {
    cycles <- sort(rep(1:n_assessments, times = 1, each = n_days))
    days <- rep(seq(1:n_days), times = n_assessments, each = 1)
    assessments_ord <- 0:(n_assessments * n_days)
    visit_values <- c("SCREENING", paste(toupper(visit_format), cycles, "DAY", days))
  }
  visit_values <- stats::reorder(factor(visit_values), assessments_ord)
}

rtpois <- function(n, lambda) {
  stats::qpois(stats::runif(n, stats::dpois(0, lambda), 1), lambda)
}

rtexp <- function(n, rate, l = NULL, r = NULL) {
  if (!is.null(l)) {
    l - log(1 - stats::runif(n)) / rate
  } else if (!is.null(r)) {
    -log(1 - stats::runif(n) * (1 - exp(-r * rate))) / rate
  } else {
    stats::rexp(n, rate)
  }
}

str_extract <- function(string, pattern) {
  regmatches(string, gregexpr(pattern, string))
}

adsl_var_labels <- c(
  STUDYID = "Study Identifier",
  USUBJID = "Unique Subject Identifier",
  SUBJID = "Subject Identifier for the Study",
  SITEID = "Study Site Identifier",
  AGE = "Age",
  SEX = "Sex",
  RACE = "Race",
  COUNTRY = "Country",
  ARM = "Description of Planned Arm",
  ARMCD = "Planned Arm Code",
  ACTARM = "Description of Actual Arm",
  ACTARMCD = "Actual Arm Code",
  REGION1 = "Geographic Region 1",
  STRATA1 = "Stratification Factor 1",
  STRATA2 = "Stratification Factor 2",
  BMRKR1 = "Continuous Level Biomarker 1",
  BMRKR2 = "Categorical Level Biomarker 2",
  SAFFL = "Safety Population Flag",
  TRTSDTM = "Datetime of First Exposure to Treatment",
  TRTEDTM = "Datetime of Last Exposure to Treatment",
  EOSSTT = "End of Study Status",
  EOTSTT = "End of Treatment Status",
  EOSDT = "End of Study Date",
  EOSDY = "End of Study Relative Day",
  DCSREAS = "Reason for Discontinuation from Study",
  DTHDT = "Date of Death"
)

common_var_labels <- c(
  PARAM = "Parameter",
  PARAMCD = "Parameter Code",
  AVISIT = "Analysis Visit",
  AVISITN = "Analysis Visit (N)",
  AVAL = "Analysis Value",
  AVALU = "Analysis Value Unit",
  BASE = "Baseline Value",
  BASE2 = "Screening Value",
  ABLFL = "Baseline Record Flag",
  ABLFL2 = "Screening Record Flag",
  CHG = "Absolute Change from Baseline",
  PCHG = "Percentage Change from Baseline",
  ANRIND = "Analysis Reference Range Indicator",
  ANRLO = "Analysis Normal Range Lower Limit",
  ANRHI = "Analysis Normal Range Upper Limit",
  ADTM = "Analysis Datetime",
  ADY = "Analysis Relative Day",
  ASTDTM = "Analysis Start Datetime"
)
```

## ADSL

```{r adsl, eval=FALSE}
generate_adsl <- function(N = 200) { # nolint
  set.seed(1)
  sys_dtm <- as.numeric(strptime("20/2/2019 11:16:16.683", "%d/%m/%Y %H:%M:%OS"))
  country_site_prob <- c(.5, .121, .077, .077, .075, .052, .046, .025, .014, .003)

  tmc_ex_adsl <- tibble::tibble(
    STUDYID = rep("AB12345", N),
    COUNTRY = sample_fct(
      c("CHN", "USA", "BRA", "PAK", "NGA", "RUS", "JPN", "GBR", "CAN", "CHE"),
      N,
      prob = country_site_prob
    ),
    SITEID = sample_fct(1:20, N, prob = rep(country_site_prob, times = 2)),
    SUBJID = paste("id", seq_len(N), sep = "-"),
    AGE = sapply(stats::rchisq(N, df = 5, ncp = 10), max, 0) + 20,
    SEX = c("F", "M") %>% sample_fct(N, prob = c(.52, .48)),
    ARMCD = c("ARM A", "ARM B", "ARM C") %>% sample_fct(N),
    ARM = dplyr::recode(
      .data$ARMCD,
      "ARM A" = "A: Drug X", "ARM B" = "B: Placebo", "ARM C" = "C: Combination"
    ),
    ACTARMCD = .data$ARMCD,
    ACTARM = .data$ARM,
    RACE = c(
      "ASIAN", "BLACK OR AFRICAN AMERICAN", "WHITE", "AMERICAN INDIAN OR ALASKA NATIVE",
      "MULTIPLE", "NATIVE HAWAIIAN OR OTHER PACIFIC ISLANDER", "OTHER", "UNKNOWN"
    ) %>%
      sample_fct(N, prob = c(.55, .23, .16, .05, .004, .003, .002, .002)),
    TRTSDTM = as.POSIXct(
      sys_dtm + sample(seq(0, study_duration_secs), size = N, replace = TRUE),
      origin = "1970-01-01"
    ),
    TRTEDTM = as.POSIXct(as.numeric(.data$TRTSDTM) + study_duration_secs, origin = "1970-01-01"),
    EOSDY = as.numeric(ceiling(difftime(.data$TRTEDTM, .data$TRTSDTM, units = "days"))),
    STRATA1 = c("A", "B", "C") %>% sample_fct(N),
    STRATA2 = c("S1", "S2") %>% sample_fct(N),
    BMRKR1 = stats::rchisq(N, 6),
    BMRKR2 = sample_fct(c("LOW", "MEDIUM", "HIGH"), N)
  )

  # associate sites with countries and regions
  tmc_ex_adsl <- tmc_ex_adsl %>%
    dplyr::mutate(
      SITEID = paste0(.data$COUNTRY, "-", .data$SITEID),
      REGION1 = factor(dplyr::case_when(
        COUNTRY %in% c("NGA") ~ "Africa",
        COUNTRY %in% c("CHN", "JPN", "PAK") ~ "Asia",
        COUNTRY %in% c("RUS") ~ "Eurasia",
        COUNTRY %in% c("GBR") ~ "Europe",
        COUNTRY %in% c("CAN", "USA") ~ "North America",
        COUNTRY %in% c("BRA") ~ "South America",
        TRUE ~ as.character(NA)
      )),
      SAFFL = factor("Y")
    ) %>%
    dplyr::mutate(USUBJID = paste(.data$STUDYID, .data$SITEID, .data$SUBJID, sep = "-"))

  # disposition related variables
  # using probability of 1 for the "DEATH" level to ensure at least one death record exists
  l_dcsreas <- list(
    choices = c(
      "ADVERSE EVENT", "DEATH", "LACK OF EFFICACY", "PHYSICIAN DECISION",
      "PROTOCOL VIOLATION", "WITHDRAWAL BY PARENT/GUARDIAN", "WITHDRAWAL BY SUBJECT"
    ),
    prob = c(.2, 1, .1, .1, .2, .1, .1)
  )
  l_dthcat_other <- list(
    choices = c(
      "Post-study reporting of death", "LOST TO FOLLOW UP", "MISSING", "SUICIDE", "UNKNOWN"
    ),
    prob = c(.1, .3, .3, .2, .1)
  )

  tmc_ex_adsl <- tmc_ex_adsl %>%
    dplyr::mutate(EOSDT = as.Date(.data$TRTEDTM)) %>%
    dplyr::mutate(EOSDY = as.numeric(ceiling(difftime(.data$TRTEDTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::mutate(EOSSTT = dplyr::case_when(
      EOSDY == max(EOSDY, na.rm = TRUE) ~ "COMPLETED",
      EOSDY < max(EOSDY, na.rm = TRUE) ~ "DISCONTINUED",
      is.na(TRTEDTM) ~ "ONGOING"
    )) %>%
    dplyr::mutate(EOTSTT = .data$EOSSTT) %>%
    dplyr::mutate(
      DCSREAS = ifelse(
        .data$EOSSTT == "DISCONTINUED",
        sample(x = l_dcsreas$choices, size = N, replace = TRUE, prob = l_dcsreas$prob),
        as.character(NA)
      )
    )

  tmc_ex_adsl <- tmc_ex_adsl %>%
    dplyr::mutate(DTHDT = dplyr::case_when(
      DCSREAS == "DEATH" ~ as.Date(.data$TRTEDTM) + sample(0:50, size = N, replace = TRUE)
    ))

  adsl_lbls_ind <- sapply(
    names(var_labels(tmc_ex_adsl)[is.na(var_labels(tmc_ex_adsl))]), function(x) which(names(adsl_var_labels) == x)
  )
  var_labels(tmc_ex_adsl[names(adsl_lbls_ind)]) <- adsl_var_labels[adsl_lbls_ind]

  save(tmc_ex_adsl, file = "data/tmc_ex_adsl.rda", compress = "xz")
}
```

## ADAE

```{r adae, eval=FALSE}
generate_adae <- function(adsl = tmc_ex_adsl,
                          max_n_aes = 5) {
  set.seed(1)
  lookup_ae <- tibble::tribble(
    ~AEBODSYS, ~AELLT, ~AEDECOD, ~AEHLT, ~AEHLGT, ~AETOXGR, ~AESOC, ~AESER, ~AEREL,
    "cl A.1", "llt A.1.1.1.1", "dcd A.1.1.1.1", "hlt A.1.1.1", "hlgt A.1.1", "1", "cl A", "N", "N",
    "cl A.1", "llt A.1.1.1.2", "dcd A.1.1.1.2", "hlt A.1.1.1", "hlgt A.1.1", "2", "cl A", "Y", "N",
    "cl B.1", "llt B.1.1.1.1", "dcd B.1.1.1.1", "hlt B.1.1.1", "hlgt B.1.1", "5", "cl B", "Y", "Y",
    "cl B.2", "llt B.2.1.2.1", "dcd B.2.1.2.1", "hlt B.2.1.2", "hlgt B.2.1", "3", "cl B", "N", "N",
    "cl B.2", "llt B.2.2.3.1", "dcd B.2.2.3.1", "hlt B.2.2.3", "hlgt B.2.2", "1", "cl B", "Y", "N",
    "cl C.1", "llt C.1.1.1.3", "dcd C.1.1.1.3", "hlt C.1.1.1", "hlgt C.1.1", "4", "cl C", "N", "Y",
    "cl C.2", "llt C.2.1.2.1", "dcd C.2.1.2.1", "hlt C.2.1.2", "hlgt C.2.1", "2", "cl C", "N", "Y",
    "cl D.1", "llt D.1.1.1.1", "dcd D.1.1.1.1", "hlt D.1.1.1", "hlgt D.1.1", "5", "cl D", "Y", "Y",
    "cl D.1", "llt D.1.1.4.2", "dcd D.1.1.4.2", "hlt D.1.1.4", "hlgt D.1.1", "3", "cl D", "N", "N",
    "cl D.2", "llt D.2.1.5.3", "dcd D.2.1.5.3", "hlt D.2.1.5", "hlgt D.2.1", "1", "cl D", "N", "Y"
  )

  aag <- utils::read.table(
    sep = ",", header = TRUE,
    text = paste(
      "NAMVAR,SRCVAR,GRPTYPE,REFNAME,REFTERM,SCOPE",
      "CQ01NAM,AEDECOD,CUSTOM,D.2.1.5.3/A.1.1.1.1 aesi,dcd D.2.1.5.3,",
      "CQ01NAM,AEDECOD,CUSTOM,D.2.1.5.3/A.1.1.1.1 aesi,dcd A.1.1.1.1,",
      "SMQ01NAM,AEDECOD,SMQ,C.1.1.1.3/B.2.2.3.1 aesi,dcd C.1.1.1.3,BROAD",
      "SMQ01NAM,AEDECOD,SMQ,C.1.1.1.3/B.2.2.3.1 aesi,dcd B.2.2.3.1,BROAD",
      "SMQ02NAM,AEDECOD,SMQ,Y.9.9.9.9/Z.9.9.9.9 aesi,dcd Y.9.9.9.9,NARROW",
      "SMQ02NAM,AEDECOD,SMQ,Y.9.9.9.9/Z.9.9.9.9 aesi,dcd Z.9.9.9.9,NARROW",
      sep = "\n"
    ), stringsAsFactors = FALSE
  )

  adae <- Map(
    function(id, sid) {
      n_aes <- sample(c(0, seq_len(max_n_aes)), 1)
      i <- sample(seq_len(nrow(lookup_ae)), n_aes, TRUE)
      dplyr::mutate(
        lookup_ae[i, ],
        USUBJID = id,
        STUDYID = sid
      )
    },
    adsl$USUBJID,
    adsl$STUDYID
  ) %>%
    Reduce(rbind, .) %>%
    `[`(c(10, 11, 1, 2, 3, 4, 5, 6, 7, 8, 9)) %>%
    dplyr::mutate(AETERM = gsub("dcd", "trm", .data$AEDECOD)) %>%
    dplyr::mutate(AESEV = dplyr::case_when(
      AETOXGR == 1 ~ "MILD",
      AETOXGR %in% c(2, 3) ~ "MODERATE",
      AETOXGR %in% c(4, 5) ~ "SEVERE"
    ))

  adae <- var_relabel(
    adae,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge adsl to be able to add AE date and study day variables
  adae <- dplyr::inner_join(adae, adsl, by = c("STUDYID", "USUBJID"), multiple = "all") %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(.data$TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(.data$TRTEDTM) ~ floor(trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ASTDTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(astdt_int = as.numeric(as.Date(.data$ASTDTM))) %>%
    dplyr::mutate(ASTDY = ceiling(as.numeric(difftime(.data$ASTDTM, .data$TRTSDTM, units = "days")))) %>%
    # add 1 to end of range incase both values passed to sample() are the same
    dplyr::mutate(AENDTM = as.POSIXct(
      (sample(.data$astdt_int:(.data$trtedt_int + 1), size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(AENDY = ceiling(as.numeric(difftime(.data$AENDTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::mutate(LDOSEDTM = as.POSIXct(
      ifelse(.data$TRTSDTM < .data$ASTDTM,
        lubridate::as_datetime(stats::runif(1, .data$TRTSDTM, .data$ASTDTM), tz = "EST"),
        .data$ASTDTM
      ),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int", -"astdt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM, .data$AETERM)

  adae <- adae %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(AESEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$AESEQ) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$ASTDTM,
      .data$AETERM,
      .data$AESEQ
    )

  outcomes <- c(
    "UNKNOWN",
    "NOT RECOVERED/NOT RESOLVED",
    "RECOVERED/RESOLVED WITH SEQUELAE",
    "RECOVERING/RESOLVING",
    "RECOVERED/RESOLVED"
  )

  adae <- adae %>%
    dplyr::mutate(AEOUT = factor(ifelse(
      .data$AETOXGR == "5",
      "FATAL",
      as.character(sample_fct(outcomes, nrow(adae), prob = c(0.1, 0.2, 0.1, 0.3, 0.3)))
    ))) %>%
    dplyr::mutate(TRTEMFL = ifelse(.data$ASTDTM >= .data$TRTSDTM, "Y", ""))

  l_aag <- split(aag, interaction(aag$NAMVAR, aag$SRCVAR, aag$GRPTYPE, drop = TRUE))

  # Create aesi flags
  l_aesi <- lapply(l_aag, function(d_adag, d_adae) {
    names(d_adag)[names(d_adag) == "REFTERM"] <- d_adag$SRCVAR[1]
    names(d_adag)[names(d_adag) == "REFNAME"] <- d_adag$NAMVAR[1]

    if (d_adag$GRPTYPE[1] == "CUSTOM") {
      d_adag <- d_adag[-which(names(d_adag) == "SCOPE")]
    } else if (d_adag$GRPTYPE[1] == "SMQ") {
      names(d_adag)[names(d_adag) == "SCOPE"] <- paste0(substr(d_adag$NAMVAR[1], 1, 5), "SC")
    }

    d_adag <- d_adag[-which(names(d_adag) %in% c("NAMVAR", "SRCVAR", "GRPTYPE"))]
    d_new <- dplyr::left_join(x = d_adae, y = d_adag, by = intersect(names(d_adae), names(d_adag)))
    d_new[, dplyr::setdiff(names(d_new), names(d_adae)), drop = FALSE]
  }, adae)

  adae <- dplyr::bind_cols(adae, l_aesi)

  actions <- c(
    "DOSE RATE REDUCED",
    "UNKNOWN",
    "NOT APPLICABLE",
    "DRUG INTERRUPTED",
    "DRUG WITHDRAWN",
    "DOSE INCREASED",
    "DOSE NOT CHANGED",
    "DOSE REDUCED",
    "NOT EVALUABLE"
  )

  tmc_ex_adae <- adae %>%
    dplyr::mutate(AEACN = factor(ifelse(
      .data$AETOXGR == "5",
      "NOT EVALUABLE",
      as.character(sample_fct(actions, nrow(adae), prob = c(0.05, 0.05, 0.05, 0.01, 0.05, 0.1, 0.45, 0.1, 0.05)))
    )))

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adae")
  formatters::var_labels(tmc_ex_adae) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adae)])
  rm(tmp_dt)

  save(tmc_ex_adae, file = "data/tmc_ex_adae.rda", compress = "xz")
}
```

## ADAETTE

```{r adaette, eval=FALSE}
generate_adaette <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  lookup_adaette <- tibble::tribble(
    ~ARM, ~CATCD, ~CAT, ~LAMBDA, ~CNSR_P,
    "ARM A", "1", "any adverse event", 1 / 80, 0.4,
    "ARM B", "1", "any adverse event", 1 / 100, 0.2,
    "ARM C", "1", "any adverse event", 1 / 60, 0.42,
    "ARM A", "2", "any serious adverse event", 1 / 100, 0.3,
    "ARM B", "2", "any serious adverse event", 1 / 150, 0.1,
    "ARM C", "2", "any serious adverse event", 1 / 80, 0.32,
    "ARM A", "3", "a grade 3-5 adverse event", 1 / 80, 0.2,
    "ARM B", "3", "a grade 3-5 adverse event", 1 / 100, 0.08,
    "ARM C", "3", "a grade 3-5 adverse event", 1 / 60, 0.23
  )

  evntdescr_sel <- "Preferred Term"

  cnsdtdscr_sel <- c(
    "Clinical Cut Off",
    "Completion or Discontinuation",
    "End of AE Reporting Period"
  )

  random_patient_data <- function(patient_info) {
    trtsdt_int <- as.numeric(as.Date(patient_info$TRTSDTM))
    trtedt_int <- ifelse(
      !is.na(patient_info$TRTEDTM),
      as.numeric(as.Date(patient_info$TRTEDTM)),
      floor(trtsdt_int + study_duration_secs / 86400)
    )
    startdt <- as.Date(patient_info$TRTSDTM)
    trtedtm <- as.POSIXct(trtedt_int * 86400, origin = "1970-01-01")
    enddts <- c(as.Date(patient_info$EOSDT), as.Date(trtedtm))
    enddts_min_index <- which.min(enddts)
    adt <- enddts[enddts_min_index]
    adtm <- as.POSIXct(adt)
    ady <- as.numeric(adt - startdt + 1)
    data.frame(
      ARM = patient_info$ARM,
      STUDYID = patient_info$STUDYID,
      SITEID = patient_info$SITEID,
      USUBJID = patient_info$USUBJID,
      PARAMCD = "AEREPTTE",
      PARAM = "Time to end of AE reporting period",
      CNSR = 0,
      AVAL = ady / 365.25,
      AVALU = "YEARS",
      EVNTDESC = ifelse(enddts_min_index == 1, "Completion or Discontinuation", "End of AE Reporting Period"),
      CNSDTDSC = NA,
      ADTM = adtm,
      ADY = ady,
      stringsAsFactors = FALSE
    )
  }

  paramcd_hy <- c("HYSTTEUL", "HYSTTEBL")
  param_hy <- c("Time to Hy's Law Elevation in relation to ULN", "Time to Hy's Law Elevation in relation to Baseline")
  param_init_list <- relvar_init(param_hy, paramcd_hy)
  adsl_hy <- dplyr::select(adsl, "STUDYID", "USUBJID", "TRTSDTM", "SITEID", "ARM")

  adaette_hy <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = as.factor(param_init_list$relvar1),
    stringsAsFactors = FALSE
  )

  adaette_hy <- dplyr::left_join(adaette_hy, adsl_hy, by = c("STUDYID", "USUBJID"), multiple = "all") %>%
    dplyr::mutate(
      PARAMCD = factor(rel_var(
        df = as.data.frame(adaette_hy),
        var_values = param_init_list$relvar2,
        related_var = "PARAM"
      ))
    ) %>%
    dplyr::mutate(
      CNSR = sample(c(0, 1), prob = c(0.1, 0.9), size = dplyr::n(), replace = TRUE),
      EVNTDESC = dplyr::if_else(
        .data$CNSR == 0,
        "First Post-Baseline Raised ALT or AST Elevation Result",
        NA_character_
      ),
      CNSDTDSC = dplyr::if_else(.data$CNSR == 0, NA_character_,
        sample(c("Last Post-Baseline ALT or AST Result", "Treatment Start"),
          prob = c(0.9, 0.1),
          size = dplyr::n(), replace = TRUE
        )
      )
    ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(ADTM = dplyr::case_when(
      .data$CNSDTDSC == "Treatment Start" ~ .data$TRTSDTM,
      TRUE ~ as.POSIXct(
        .data$TRTSDTM + sample(seq(0, study_duration_secs), size = dplyr::n(), replace = TRUE),
        origin = "1970-01-01"
      )
    )) %>%
    dplyr::mutate(
      STARTDT = as.Date(.data$TRTSDTM),
      ADT = as.Date(.data$ADTM),
      ADY = as.numeric(.data$ADT - .data$STARTDT + 1),
      AVAL = .data$ADY / 7,
      AVALU = "WEEKS"
    )

  adaette_hy <- dplyr::select(adaette_hy, -"TRTSDTM", -"ADT", -"STARTDT")

  random_ae_data <- function(lookup_info, patient_info, patient_data) {
    cnsr <- sample(c(0, 1), 1, prob = c(1 - lookup_info$CNSR_P, lookup_info$CNSR_P))
    ae_rep_tte <- patient_data$AVAL[patient_data$PARAMCD == "AEREPTTE"]
    data.frame(
      ARM = rep(patient_data$ARM, 2),
      STUDYID = rep(patient_data$STUDYID, 2),
      SITEID = rep(patient_data$SITEID, 2),
      USUBJID = rep(patient_data$USUBJID, 2),
      PARAMCD = c(
        paste0("AETTE", lookup_info$CATCD),
        paste0("AETOT", lookup_info$CATCD)
      ),
      PARAM = c(
        paste("Time to first occurrence of", lookup_info$CAT),
        paste("Number of occurrences of", lookup_info$CAT)
      ),
      CNSR = c(
        cnsr,
        NA
      ),
      AVAL = c(
        ifelse(cnsr == 1, ae_rep_tte, rtexp(1, lookup_info$LAMBDA * 365.25, r = ae_rep_tte)),
        ifelse(cnsr == 1, 0, rtpois(1, lookup_info$LAMBDA * 365.25))
      ),
      AVALU = c(
        "YEARS",
        NA
      ),
      EVNTDESC = c(
        ifelse(cnsr == 0, sample(evntdescr_sel, 1), ""),
        NA
      ),
      CNSDTDSC = c(
        ifelse(cnsr == 1, sample(cnsdtdscr_sel, 1), ""),
        NA
      ),
      stringsAsFactors = FALSE
    ) %>% dplyr::mutate(
      ADY = dplyr::if_else(is.na(.data$AVALU), NA_real_, ceiling(.data$AVAL * 365.25)),
      ADTM = dplyr::if_else(
        is.na(.data$AVALU),
        as.POSIXct(NA),
        as.POSIXct(patient_info$TRTSDTM) + as.difftime(.data$ADY, units = "days")
      )
    )
  }

  adaette <- split(adsl, adsl$USUBJID) %>%
    lapply(function(patient_info) {
      patient_data <- random_patient_data(patient_info)
      lookup_arm <- lookup_adaette %>%
        dplyr::filter(.data$ARM == as.character(patient_info$ARMCD))
      ae_data <- split(lookup_arm, lookup_arm$CATCD) %>%
        lapply(random_ae_data, patient_data = patient_data, patient_info = patient_info) %>%
        Reduce(rbind, .)
      dplyr::bind_rows(patient_data, ae_data)
    }) %>%
    Reduce(rbind, .)

  adaette <- var_relabel(
    adaette,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  adaette <- rbind(adaette, adaette_hy)

  tmc_ex_adaette <- adsl %>%
    dplyr::inner_join(
      dplyr::select(adaette, -"SITEID", -"ARM"),
      by = c("STUDYID", "USUBJID"),
      multiple = "all"
    ) %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::arrange(.data$ADTM) %>%
    dplyr::mutate(TTESEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$TTESEQ) %>%
    dplyr::mutate(PARAM = as.factor(.data$PARAM)) %>%
    dplyr::mutate(PARAMCD = as.factor(.data$PARAMCD)) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$ADTM,
      .data$TTESEQ
    )

  save(tmc_ex_adaette, file = "data/tmc_ex_adaette.rda", compress = "xz")
}
```

## ADCM

```{r adcm, eval=FALSE}
generate_adcm <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  max_n_cms <- 10L

  lookup_cm <- tibble::tribble(
    ~CMCLAS, ~CMDECOD, ~ATIREL,
    "medcl A", "medname A_1/3", "PRIOR",
    "medcl A", "medname A_2/3", "CONCOMITANT",
    "medcl A", "medname A_3/3", "CONCOMITANT",
    "medcl B", "medname B_1/4", "CONCOMITANT",
    "medcl B", "medname B_2/4", "PRIOR",
    "medcl B", "medname B_3/4", "PRIOR",
    "medcl B", "medname B_4/4", "CONCOMITANT",
    "medcl C", "medname C_1/2", "CONCOMITANT",
    "medcl C", "medname C_2/2", "CONCOMITANT"
  )

  adcm <- Map(function(id, sid) {
    n_cms <- sample(c(0, seq_len(max_n_cms)), 1)
    i <- sample(seq_len(nrow(lookup_cm)), n_cms, TRUE)
    dplyr::mutate(
      lookup_cm[i, ],
      USUBJID = id,
      STUDYID = sid
    )
  }, adsl$USUBJID, adsl$STUDYID) %>%
    Reduce(rbind, .) %>%
    `[`(c(4, 5, 1, 2, 3)) %>%
    dplyr::mutate(CMCAT = .data$CMCLAS)

  adcm <- var_relabel(
    adcm,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge adsl to be able to add CM date and study day variables
  adcm <- dplyr::inner_join(
    adcm,
    adsl,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ASTDTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(astdt_int = as.numeric(as.Date(.data$ASTDTM))) %>%
    dplyr::mutate(ASTDY = ceiling(as.numeric(difftime(.data$ASTDTM, .data$TRTSDTM, units = "days")))) %>%
    # add 1 to end of range incase both values passed to sample() are the same
    dplyr::mutate(AENDTM = as.POSIXct(
      (
        sample(.data$astdt_int:(.data$trtedt_int + 1), size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(AENDY = ceiling(as.numeric(difftime(.data$AENDTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int", -"astdt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM)

  tmc_ex_adcm <- adcm %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(CMSEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$CMSEQ) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM, .data$CMSEQ) %>%
    dplyr::mutate(
      ATC1 = paste("ATCCLAS1", substr(.data$CMDECOD, 9, 9)),
      ATC2 = paste("ATCCLAS2", substr(.data$CMDECOD, 9, 9)),
      ATC3 = paste("ATCCLAS3", substr(.data$CMDECOD, 9, 9)),
      ATC4 = paste("ATCCLAS4", substr(.data$CMDECOD, 9, 9))
    ) %>%
    dplyr::mutate(CMINDC = sample(c(
      "Nausea", "Hypertension", "Urticaria", "Fever",
      "Asthma", "Infection", "Diabete", "Diarrhea", "Pneumonia"
    ), dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMDOSE = sample(1:99, dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMTRT = substr(.data$CMDECOD, 9, 13)) %>%
    dplyr::mutate(CMDOSU = sample(c(
      "ug/mL", "ug/kg/day", "%", "uL", "DROP",
      "umol/L", "mg", "mg/breath", "ug"
    ), dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMROUTE = sample(c(
      "INTRAVENOUS", "ORAL", "NASAL",
      "INTRAMUSCULAR", "SUBCUTANEOUS", "INHALED", "RECTAL", "UNKNOWN"
    ), dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMDOSFRQ = sample(c(
      "Q4W", "QN", "Q4H", "UNKNOWN", "TWICE",
      "Q4H", "QD", "TID", "4 TIMES PER MONTH"
    ), dplyr::n(), replace = TRUE))

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adcm")
  formatters::var_labels(tmc_ex_adcm) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adcm)])
  rm(tmp_dt)

  save(tmc_ex_adcm, file = "data/tmc_ex_adcm.rda", compress = "xz")
}
```

## ADEG

```{r adeg, eval=FALSE}
generate_adeg <- function(adsl = tmc_ex_adsl,
                          n_assessments = 3L,
                          n_days = 3L,
                          max_n_eg = 5L) {
  set.seed(1)
  egcat <- c("INTERVAL", "INTERVAL", "MEASUREMENT", "FINDING")
  param <- c("QT Duration", "RR Duration", "Heart Rate", "ECG Interpretation")
  paramcd <- c("QT", "RR", "HR", "ECGINTP")
  paramu <- c("msec", "msec", "beats/min", "")
  visit_format <- "WEEK"

  egcat_init_list <- relvar_init(param, egcat)
  param_init_list <- relvar_init(param, paramcd)
  unit_init_list <- relvar_init(param, paramu)

  adeg <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = as.factor(param_init_list$relvar1),
    AVISIT = visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days),
    stringsAsFactors = FALSE
  )

  adeg$EGCAT <- as.factor(rel_var(
    df = adeg,
    var_name = "EGCAT",
    var_values = egcat_init_list$relvar2,
    related_var = "PARAM"
  ))

  adeg$PARAMCD <- as.factor(rel_var(
    df = adeg,
    var_name = "PARAMCD",
    var_values = param_init_list$relvar2,
    related_var = "PARAM"
  ))

  adeg <- adeg %>% dplyr::mutate(AVAL = dplyr::case_when(
    .data$PARAMCD == "QT" ~ stats::rnorm(nrow(adeg), mean = 350, sd = 100),
    .data$PARAMCD == "RR" ~ stats::rnorm(nrow(adeg), mean = 1050, sd = 300),
    .data$PARAMCD == "HR" ~ stats::rnorm(nrow(adeg), mean = 70, sd = 20),
    .data$PARAMCD == "ECGINTP" ~ NA_real_
  ))

  adeg <- adeg %>%
    dplyr::mutate(EGTESTCD = .data$PARAMCD) %>%
    dplyr::mutate(EGTEST = .data$PARAM)

  adeg <- adeg %>% dplyr::mutate(AVISITN = dplyr::case_when(
    AVISIT == "SCREENING" ~ -1,
    AVISIT == "BASELINE" ~ 0,
    (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
    TRUE ~ NA_real_
  ))

  adeg$AVALU <- as.factor(rel_var(
    df = adeg,
    var_name = "AVALU",
    var_values = unit_init_list$relvar2,
    related_var = "PARAM"
  ))

  adeg <- adeg[order(adeg$STUDYID, adeg$USUBJID, adeg$PARAMCD, adeg$AVISITN), ]

  adeg <- Reduce(rbind, lapply(split(adeg, adeg$USUBJID), function(x) {
    x$STUDYID <- adsl$STUDYID[which(adsl$USUBJID == x$USUBJID[1])]
    x$ABLFL <- ifelse(toupper(visit_format) == "WEEK" & x$AVISIT == "BASELINE",
      "Y",
      ifelse(toupper(visit_format) == "CYCLE" & x$AVISIT == "CYCLE 1 DAY 1", "Y", "")
    )
    x
  }))

  adeg$BASE <- ifelse(adeg$AVISITN >= 0, retain(adeg, adeg$AVAL, adeg$ABLFL == "Y"), adeg$AVAL)

  adeg <- adeg %>% dplyr::mutate(ANRLO = dplyr::case_when(
    .data$PARAMCD == "QT" ~ 200,
    .data$PARAMCD == "RR" ~ 600,
    .data$PARAMCD == "HR" ~ 40,
    .data$PARAMCD == "ECGINTP" ~ NA_real_
  ))

  adeg <- adeg %>% dplyr::mutate(ANRHI = dplyr::case_when(
    .data$PARAMCD == "QT" ~ 500,
    .data$PARAMCD == "RR" ~ 1500,
    .data$PARAMCD == "HR" ~ 100,
    .data$PARAMCD == "ECGINTP" ~ NA_real_
  ))

  adeg <- adeg %>% dplyr::mutate(ANRIND = factor(dplyr::case_when(
    .data$AVAL < .data$ANRLO ~ "LOW",
    .data$AVAL >= .data$ANRLO & .data$AVAL <= .data$ANRHI ~ "NORMAL",
    .data$AVAL > .data$ANRHI ~ "HIGH"
  )))

  adeg <- adeg %>%
    dplyr::mutate(CHG = ifelse(.data$AVISITN > 0, .data$AVAL - .data$BASE, NA)) %>%
    dplyr::mutate(PCHG = ifelse(.data$AVISITN > 0, 100 * (.data$CHG / .data$BASE), NA)) %>%
    dplyr::mutate(BASETYPE = "LAST") %>%
    dplyr::group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    dplyr::mutate(BNRIND = .data$ANRIND[.data$ABLFL == "Y"]) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(ATPTN = 1) %>%
    dplyr::mutate(DTYPE = NA)

  adeg$ANRIND <- factor(adeg$ANRIND, levels = c("LOW", "NORMAL", "HIGH"))
  adeg$BNRIND <- factor(adeg$BNRIND, levels = c("LOW", "NORMAL", "HIGH"))

  adeg <- var_relabel(
    adeg,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  adeg <- dplyr::inner_join(
    adsl,
    adeg,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::group_by(USUBJID, AVISIT) %>%
    dplyr::mutate(ADTM = as.POSIXct(
      (sample(unique(.data$trtsdt_int):unique(.data$trtedt_int), size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(ADY = ceiling(as.numeric(difftime(.data$ADTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  adeg <- adeg %>%
    dplyr::mutate(ASPID = sample(seq_len(dplyr::n()))) %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(EGSEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$EGSEQ) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$BASETYPE,
      .data$AVISITN,
      .data$ATPTN,
      .data$DTYPE,
      .data$ADTM,
      .data$EGSEQ,
      .data$ASPID
    )

  adeg <- adeg %>% dplyr::mutate(ONTRTFL = factor(dplyr::case_when(
    is.na(.data$TRTSDTM) ~ "",
    is.na(.data$ADTM) ~ "Y",
    (.data$ADTM < .data$TRTSDTM) ~ "",
    (.data$ADTM > .data$TRTEDTM) ~ "",
    TRUE ~ "Y"
  )))

  adeg <- adeg %>% dplyr::mutate(AVALC = ifelse(
    .data$PARAMCD == "ECGINTP",
    as.character(sample_fct(c("ABNORMAL", "NORMAL"), nrow(adeg), prob = c(0.25, 0.75))),
    as.character(.data$AVAL)
  ))

  adeg <- adeg %>%
    dplyr::mutate(row_check = seq_len(nrow(adeg)))

  get_groups <- function(data,
                         minimum) {
    data <- data %>%
      dplyr::group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
      dplyr::arrange(.data$ADTM, .data$ASPID, .data$EGSEQ) %>%
      dplyr::filter(
        (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
          (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
      ) %>%
      {
        if (minimum == TRUE) {
          dplyr::filter(., .data$AVAL == min(.data$AVAL)) %>%
            dplyr::mutate(., DTYPE = "MINIMUM", AVISIT = "POST-BASELINE MINIMUM")
        } else {
          dplyr::filter(., .data$AVAL == max(.data$AVAL)) %>%
            dplyr::mutate(., DTYPE = "MAXIMUM", AVISIT = "POST-BASELINE MAXIMUM")
        }
      } %>%
      dplyr::slice(1) %>%
      dplyr::ungroup()

    return(data)
  }

  adeg <- rbind(adeg, get_groups(adeg, TRUE), get_groups(adeg, FALSE)) %>%
    dplyr::arrange(.data$row_check) %>%
    dplyr::group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    dplyr::arrange(.data$AVISIT, .by_group = TRUE) %>%
    dplyr::ungroup()

  adeg <- adeg[, -which(names(adeg) %in% c("row_check"))]

  flag_variables <- function(data, worst_obs) {
    data_compare <- data %>%
      dplyr::mutate(row_check = seq_len(nrow(data)))

    data <- data_compare %>%
      {
        if (worst_obs == FALSE) {
          dplyr::group_by(., .data$USUBJID, .data$PARAMCD, .data$BASETYPE, .data$AVISIT) %>%
            dplyr::arrange(., .data$ADTM, .data$ASPID, .data$EGSEQ)
        } else {
          dplyr::group_by(., .data$USUBJID, .data$PARAMCD, .data$BASETYPE)
        }
      } %>%
      dplyr::filter(
        .data$AVISITN > 0 & (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM) &
          is.na(.data$DTYPE)
      ) %>%
      {
        if (worst_obs == TRUE) {
          dplyr::arrange(., .data$AVALC) %>% dplyr::filter(., ifelse(
            .data$PARAMCD == "ECGINTP",
            ifelse(.data$AVALC == "ABNORMAL", .data$AVALC == "ABNORMAL", .data$AVALC == "NORMAL"),
            .data$AVAL == min(.data$AVAL)
          ))
        } else {
          dplyr::filter(., ifelse(
            .data$PARAMCD == "ECGINTP",
            .data$AVALC == "ABNORMAL" | .data$AVALC == "NORMAL",
            .data$AVAL == min(.data$AVAL)
          ))
        }
      } %>%
      dplyr::slice(1) %>%
      {
        if (worst_obs == TRUE) {
          dplyr::mutate(., new_var = dplyr::case_when(
            (.data$AVALC == "ABNORMAL" | .data$AVALC == "NORMAL") ~ "Y",
            (!is.na(.data$AVAL) & is.na(.data$DTYPE)) ~ "Y",
            TRUE ~ ""
          ))
        } else {
          dplyr::mutate(., new_var = dplyr::case_when(
            (.data$AVALC == "ABNORMAL" | .data$AVALC == "NORMAL") ~ "Y",
            (!is.na(.data$AVAL) & is.na(.data$DTYPE)) ~ "Y",
            TRUE ~ ""
          ))
        }
      } %>%
      dplyr::ungroup()

    data_compare$new_var <- ifelse(data_compare$row_check %in% data$row_check, "Y", "")
    data_compare <- data_compare[, -which(names(data_compare) %in% c("row_check"))]

    return(data_compare)
  }

  adeg <- flag_variables(adeg, FALSE) %>% dplyr::rename(WORS01FL = "new_var")
  adeg <- flag_variables(adeg, TRUE) %>% dplyr::rename(WORS02FL = "new_var")

  adeg <- adeg %>% dplyr::mutate(ANL01FL = factor(ifelse(
    (.data$ABLFL == "Y" | (is.na(.data$DTYPE) & .data$WORS01FL == "Y")) &
      (.data$AVISIT != "SCREENING"),
    "Y",
    ""
  )))

  tmc_ex_adeg <- adeg %>%
    dplyr::group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    dplyr::mutate(BASEC = ifelse(
      .data$PARAMCD == "ECGINTP",
      .data$AVALC[.data$AVISIT == "BASELINE"],
      as.character(.data$BASE)
    )) %>%
    dplyr::mutate(ANL03FL = dplyr::case_when(
      .data$DTYPE == "MINIMUM" ~ "Y",
      .data$ABLFL == "Y" & .data$PARAMCD != "ECGINTP" ~ "Y",
      TRUE ~ ""
    )) %>%
    dplyr::mutate(ANL04FL = dplyr::case_when(
      .data$DTYPE == "MAXIMUM" ~ "Y",
      .data$ABLFL == "Y" & .data$PARAMCD != "ECGINTP" ~ "Y",
      TRUE ~ ""
    )) %>%
    dplyr::ungroup()

  save(tmc_ex_adeg, file = "data/tmc_ex_adeg.rda", compress = "xz")
}
```

## ADEX

```{r adex, eval=FALSE}
generate_adex <- function(adsl = tmc_ex_adsl,
                          n_assessments = 3L,
                          n_days = 3L,
                          max_n_exs = 3L) {
  set.seed(1)
  param <- c(
    "Dose administered during constant dosing interval",
    "Number of doses administered during constant dosing interval",
    "Total dose administered",
    "Total number of doses administered"
  )
  paramcd <- c("DOSE", "NDOSE", "TDOSE", "TNDOSE")
  paramu <- c("mg", " ", "mg", " ")
  parcat1 <- c("INDIVIDUAL", "OVERALL")
  parcat2 <- c("Drug A", "Drug B")
  visit_format <- "WEEK"

  param_init_list <- relvar_init(param, paramcd)
  unit_init_list <- relvar_init(param, paramu)

  adex <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = c(
      rep(
        param_init_list$relvar1[1],
        length(levels(visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days)))
      ),
      rep(
        param_init_list$relvar1[2],
        length(levels(visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days)))
      ),
      param_init_list$relvar1[3:4]
    ),
    stringsAsFactors = FALSE
  )

  adex$PARAMCD <- as.factor(rel_var(
    df = adex,
    var_name = "PARAMCD",
    var_values = param_init_list$relvar2,
    related_var = "PARAM"
  ))

  adex$AVALU <- as.factor(rel_var(
    df = adex,
    var_name = "AVALU",
    var_values = unit_init_list$relvar2,
    related_var = "PARAM"
  ))

  adex <- adex %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(PARCAT_ind = sample(c(1, 2), size = 1)) %>%
    dplyr::mutate(PARCAT2 = ifelse(.data$PARCAT_ind == 1, parcat2[1], parcat2[2])) %>%
    dplyr::select(-"PARCAT_ind")

  adex <- adex %>% dplyr::mutate(PARCAT1 = dplyr::case_when(
    (.data$PARAMCD == "TNDOSE" | .data$PARAMCD == "TDOSE") ~ "OVERALL",
    .data$PARAMCD == "DOSE" | .data$PARAMCD == "NDOSE" ~ "INDIVIDUAL"
  ))

  adex_visit <- adex %>%
    dplyr::filter(.data$PARAMCD == "DOSE" | .data$PARAMCD == "NDOSE") %>%
    dplyr::mutate(
      AVISIT = rep(visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days), 2)
    )

  adex <- dplyr::left_join(
    adex %>%
      dplyr::group_by(
        .data$USUBJID,
        .data$STUDYID,
        .data$PARAM,
        .data$PARAMCD,
        .data$AVALU,
        .data$PARCAT1,
        .data$PARCAT2
      ) %>%
      dplyr::mutate(id = dplyr::row_number()),
    adex_visit %>%
      dplyr::group_by(
        .data$USUBJID,
        .data$STUDYID,
        .data$PARAM,
        .data$PARAMCD,
        .data$AVALU,
        .data$PARCAT1,
        .data$PARCAT2
      ) %>%
      dplyr::mutate(id = dplyr::row_number()),
    by = c("USUBJID", "STUDYID", "PARCAT1", "PARCAT2", "id", "PARAMCD", "PARAM", "AVALU")
  ) %>%
    dplyr::select(-"id")

  adex <- adex %>% dplyr::mutate(AVISITN = dplyr::case_when(
    AVISIT == "SCREENING" ~ -1,
    AVISIT == "BASELINE" ~ 0,
    (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
    TRUE ~ 999000
  ))


  adex2 <- split(adex, adex$USUBJID) %>%
    lapply(function(pinfo) {
      pinfo %>%
        dplyr::filter(.data$PARAMCD == "DOSE") %>%
        dplyr::group_by(.data$USUBJID, .data$PARCAT2, .data$AVISIT) %>%
        dplyr::mutate(changeind = dplyr::case_when(
          .data$AVISIT == "SCREENING" ~ 0,
          .data$AVISIT != "SCREENING" ~ sample(c(-1, 0, 1),
            size = 1,
            prob = c(0.25, 0.5, 0.25),
            replace = TRUE
          )
        )) %>%
        dplyr::ungroup() %>%
        dplyr::group_by(.data$USUBJID, .data$PARCAT2) %>%
        dplyr::mutate(
          csum = cumsum(.data$changeind),
          changeind = dplyr::case_when(
            .data$csum <= -3 ~ sample(c(0, 1), size = 1, prob = c(0.5, 0.5)),
            .data$csum >= 3 ~ sample(c(0, -1), size = 1, prob = c(0.5, 0.5)),
            TRUE ~ .data$changeind
          )
        ) %>%
        dplyr::mutate(csum = cumsum(.data$changeind)) %>%
        dplyr::ungroup() %>%
        dplyr::group_by(.data$USUBJID, .data$PARCAT2, .data$AVISIT) %>%
        dplyr::mutate(AVAL = dplyr::case_when(
          .data$csum == -2 ~ 480,
          .data$csum == -1 ~ 720,
          .data$csum == 0 ~ 960,
          .data$csum == 1 ~ 1200,
          .data$csum == 2 ~ 1440
        )) %>%
        dplyr::select(-c("csum", "changeind")) %>%
        dplyr::ungroup()
    }) %>%
    Reduce(rbind, .)

  adextmp <- dplyr::full_join(adex2, adex, by = names(adex))
  adex <- adextmp %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(AVAL = ifelse(.data$PARAMCD == "NDOSE", 1, .data$AVAL)) %>%
    dplyr::mutate(AVAL = ifelse(
      .data$PARAMCD == "TNDOSE",
      sum(.data$AVAL[.data$PARAMCD == "NDOSE"]),
      .data$AVAL
    )) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(.data$USUBJID, .data$STUDYID, .data$PARCAT2) %>%
    dplyr::mutate(AVAL = ifelse(
      .data$PARAMCD == "TDOSE",
      sum(.data$AVAL[.data$PARAMCD == "DOSE"]),
      .data$AVAL
    ))

  adex <- var_relabel(
    adex,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  adex <- dplyr::inner_join(adsl, adex, by = c("STUDYID", "USUBJID"), multiple = "all") %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ASTDTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(astdt_int = as.numeric(as.Date(.data$ASTDTM))) %>%
    dplyr::mutate(AENDTM = as.POSIXct(
      (sample(.data$astdt_int:(.data$trtedt_int + 1), size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int", -"astdt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM)


  adex <- adex %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(EXSEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$EXSEQ) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$ASTDTM,
      .data$AVISITN,
      .data$EXSEQ
    )

  adex <- adex %>%
    dplyr::mutate(EXDOSFRQ = dplyr::case_when(
      PARCAT1 == "INDIVIDUAL" ~ "ONCE",
      TRUE ~ ""
    ))

  adex <- adex %>%
    dplyr::mutate(EXROUTE = dplyr::case_when(
      PARCAT1 == "INDIVIDUAL" ~ sample(c("INTRAVENOUS", "SUBCUTANEOUS"),
        nrow(adex),
        replace = TRUE,
        prob = c(0.9, 0.1)
      ),
      TRUE ~ ""
    ))

  adex <- adex %>% dplyr::mutate(VISIT = AVISIT)

  visit_levels <- str_extract(levels(adex$VISIT), pattern = "[0-9]+")
  vl_extracted <- vapply(visit_levels, function(x) as.numeric(x[2]), numeric(1))
  vl_extracted <- c(-1, 1, vl_extracted[!is.na(vl_extracted)])

  adex <- adex %>%
    dplyr::mutate(VISITDY = as.numeric(as.character(factor(VISIT, labels = vl_extracted))))

  adex <- adex %>%
    dplyr::mutate(
      EXSTDTC = lubridate::as_datetime(TRTSDTM) + lubridate::days(VISITDY),
      EXENDTC = EXSTDTC + lubridate::hours(1),
      EXSTDY = VISITDY,
      EXENDY = VISITDY
    )

  adex <- adex %>%
    dplyr::group_by(SUBJID) %>%
    dplyr::mutate(TRTEDTM = max(EXENDTC, na.rm = TRUE)) %>%
    dplyr::ungroup()

  adex <- adex %>%
    dplyr::mutate(
      TRTSDT = lubridate::as_date(TRTSDTM),
      TRTEDT = lubridate::as_date(TRTEDTM)
    )

  tmc_ex_adex <- adex %>%
    dplyr::mutate(
      ASTDY = EXSTDY,
      AENDY = EXENDY,
      ASTDTM = EXSTDTC,
      AENDTM = EXENDTC
    )

  save(tmc_ex_adex, file = "data/tmc_ex_adex.rda", compress = "xz")
}
```

## ADLB

```{r adlb, eval=FALSE}
generate_adlb <- function(adsl = tmc_ex_adsl,
                          max_n_lbs = 5L) {
  set.seed(1)
  lbcat <- c("CHEMISTRY", "CHEMISTRY", "IMMUNOLOGY")
  param <- c(
    "Alanine Aminotransferase Measurement",
    "C-Reactive Protein Measurement",
    "Immunoglobulin A Measurement"
  )
  paramcd <- c("ALT", "CRP", "IGA")
  paramu <- c("U/L", "mg/L", "g/L")
  aval_mean <- c(20, 1, 2)
  visit_format <- "WEEK"
  n_assessments <- 5L
  n_days <- 5L

  # validate and initialize related variables
  lbcat_init_list <- relvar_init(param, lbcat)
  param_init_list <- relvar_init(param, paramcd)
  unit_init_list <- relvar_init(param, paramu)

  adlb <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = as.factor(param_init_list$relvar1),
    AVISIT = visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days),
    stringsAsFactors = FALSE
  )

  # assign AVAL based on different test
  adlb <- adlb %>%
    dplyr::mutate(AVAL = stats::rnorm(nrow(adlb), mean = 1, sd = 0.2)) %>%
    dplyr::left_join(data.frame(PARAM = param, ADJUST = aval_mean), by = "PARAM") %>%
    dplyr::mutate(AVAL = .data$AVAL * .data$ADJUST) %>%
    dplyr::select(-"ADJUST")

  # assign related variable values: PARAMxLBCAT are related
  adlb$LBCAT <- as.factor(rel_var(
    df = adlb,
    var_name = "LBCAT",
    var_values = lbcat_init_list$relvar2,
    related_var = "PARAM"
  ))

  # assign related variable values: PARAMxPARAMCD are related
  adlb$PARAMCD <- as.factor(rel_var(
    df = adlb,
    var_name = "PARAMCD",
    var_values = param_init_list$relvar2,
    related_var = "PARAM"
  ))

  adlb$AVALU <- as.factor(rel_var(
    df = adlb,
    var_name = "AVALU",
    var_values = unit_init_list$relvar2,
    related_var = "PARAM"
  ))

  adlb <- adlb %>% dplyr::mutate(AVISITN = dplyr::case_when(
    AVISIT == "SCREENING" ~ -1,
    AVISIT == "BASELINE" ~ 0,
    (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
    TRUE ~ NA_real_
  ))

  adlb <- adlb %>%
    dplyr::mutate(AVISITN = dplyr::case_when(
      AVISIT == "SCREENING" ~ -1,
      AVISIT == "BASELINE" ~ 0,
      (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
      TRUE ~ NA_real_
    ))

  # order to prepare for change from screening and baseline values
  adlb <- adlb[order(adlb$STUDYID, adlb$USUBJID, adlb$PARAMCD, adlb$AVISITN), ]

  adlb <- Reduce(rbind, lapply(split(adlb, adlb$USUBJID), function(x) {
    x$STUDYID <- adsl$STUDYID[which(adsl$USUBJID == x$USUBJID[1])]
    x$ABLFL2 <- ifelse(x$AVISIT == "SCREENING", "Y", "")
    x$ABLFL <- ifelse(toupper(visit_format) == "WEEK" & x$AVISIT == "BASELINE",
      "Y",
      ifelse(toupper(visit_format) == "CYCLE" & x$AVISIT == "CYCLE 1 DAY 1", "Y", "")
    )
    x
  }))

  adlb$BASE <- ifelse(adlb$ABLFL2 != "Y", retain(adlb, adlb$AVAL, adlb$ABLFL == "Y"), NA)

  anrind_choices <- c("HIGH", "LOW", "NORMAL")

  adlb <- adlb %>%
    dplyr::mutate(BASETYPE = "LAST") %>%
    dplyr::mutate(ANRIND = sample_fct(anrind_choices, nrow(adlb), prob = c(0.1, 0.1, 0.8))) %>%
    dplyr::mutate(ANRLO = dplyr::case_when(
      .data$PARAMCD == "ALT" ~ 7,
      .data$PARAMCD == "CRP" ~ 8,
      .data$PARAMCD == "IGA" ~ 0.8
    )) %>%
    dplyr::mutate(ANRHI = dplyr::case_when(
      .data$PARAMCD == "ALT" ~ 55,
      .data$PARAMCD == "CRP" ~ 10,
      .data$PARAMCD == "IGA" ~ 3
    )) %>%
    dplyr::mutate(DTYPE = NA) %>%
    dplyr::mutate(ATOXGR = factor(dplyr::case_when(
      .data$ANRIND == "LOW" ~ sample(
        c("-1", "-2", "-3", "-4", "-5"),
        nrow(adlb),
        replace = TRUE,
        prob = c(0.30, 0.25, 0.20, 0.15, 0)
      ),
      .data$ANRIND == "HIGH" ~ sample(
        c("1", "2", "3", "4", "5"),
        nrow(adlb),
        replace = TRUE,
        prob = c(0.30, 0.25, 0.20, 0.15, 0)
      ),
      .data$ANRIND == "NORMAL" ~ "0"
    ))) %>%
    dplyr::group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    dplyr::mutate(BTOXGR = .data$ATOXGR[.data$ABLFL == "Y"]) %>%
    dplyr::ungroup()

  # High and low descriptions of the different PARAMCD values
  # This is currently hard coded as the GDSR does not have these descriptions yet
  grade_lookup <- tibble::tribble(
    ~PARAMCD, ~ATOXDSCL, ~ATOXDSCH,
    "ALB", "Hypoalbuminemia", NA_character_,
    "ALKPH", NA_character_, "Alkaline phosphatase increased",
    "ALT", NA_character_, "Alanine aminotransferase increased",
    "AST", NA_character_, "Aspartate aminotransferase increased",
    "BILI", NA_character_, "Blood bilirubin increased",
    "CA", "Hypocalcemia", "Hypercalcemia",
    "CHOLES", NA_character_, "Cholesterol high",
    "CK", NA_character_, "CPK increased",
    "CREAT", NA_character_, "Creatinine increased",
    "CRP", NA_character_, "C reactive protein increased",
    "GGT", NA_character_, "GGT increased",
    "GLUC", "Hypoglycemia", "Hyperglycemia",
    "HGB", "Anemia", "Hemoglobin increased",
    "IGA", NA_character_, "Immunoglobulin A increased",
    "POTAS", "Hypokalemia", "Hyperkalemia",
    "LYMPH", "CD4 lymphocytes decreased", NA_character_,
    "PHOS", "Hypophosphatemia", NA_character_,
    "PLAT", "Platelet count decreased", NA_character_,
    "SODIUM", "Hyponatremia", "Hypernatremia",
    "WBC", "White blood cell decreased", "Leukocytosis",
  )

  # merge grade_lookup onto adlb
  adlb <- dplyr::left_join(adlb, grade_lookup, by = "PARAMCD")

  adlb <- var_relabel(
    adlb,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge adsl to be able to add LB date and study day variables
  adlb <- dplyr::inner_join(
    adsl,
    adlb,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ADTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  adlb <- adlb %>%
    dplyr::mutate(ASPID = sample(seq_len(dplyr::n()))) %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(LBSEQ = seq_len(dplyr::n())) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$BASETYPE,
      .data$AVISITN,
      .data$DTYPE,
      .data$ADTM,
      .data$LBSEQ,
      .data$ASPID
    )

  adlb <- adlb %>% dplyr::mutate(ONTRTFL = factor(dplyr::case_when(
    is.na(.data$TRTSDTM) ~ "",
    is.na(.data$ADTM) ~ "Y",
    (.data$ADTM < .data$TRTSDTM) ~ "",
    (.data$ADTM > .data$TRTEDTM) ~ "",
    TRUE ~ "Y"
  )))

  flag_variables <- function(data,
                             apply_grouping,
                             apply_filter,
                             apply_mutate) {
    data_compare <- data %>%
      dplyr::mutate(row_check = seq_len(nrow(data)))

    data <- data_compare %>%
      {
        if (apply_grouping == TRUE) {
          dplyr::group_by(., .data$USUBJID, .data$PARAMCD, .data$BASETYPE, .data$AVISIT)
        } else {
          dplyr::group_by(., .data$USUBJID, .data$PARAMCD, .data$BASETYPE)
        }
      } %>%
      dplyr::arrange(.data$ADTM, .data$ASPID, .data$LBSEQ) %>%
      {
        if (apply_filter == TRUE) {
          dplyr::filter(
            .,
            (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
              (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
          ) %>%
            dplyr::filter(.data$ATOXGR == max(as.numeric(as.character(.data$ATOXGR))))
        } else if (apply_filter == FALSE) {
          dplyr::filter(
            .,
            (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
              (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
          ) %>%
            dplyr::filter(.data$ATOXGR == min(as.numeric(as.character(.data$ATOXGR))))
        } else {
          dplyr::filter(
            .,
            .data$AVAL == min(.data$AVAL) &
              (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
              (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
          )
        }
      } %>%
      dplyr::slice(1) %>%
      {
        if (apply_mutate == TRUE) {
          dplyr::mutate(., new_var = ifelse(is.na(.data$DTYPE), "Y", ""))
        } else {
          dplyr::mutate(., new_var = ifelse(is.na(.data$AVAL) == FALSE & is.na(.data$DTYPE), "Y", ""))
        }
      } %>%
      dplyr::ungroup()

    data_compare$new_var <- ifelse(data_compare$row_check %in% data$row_check, "Y", "")

    data_compare <- data_compare[, -which(names(data_compare) %in% c("row_check"))]

    return(data_compare)
  }

  adlb <- flag_variables(adlb, TRUE, "ELSE", FALSE) %>% dplyr::rename(WORS01FL = "new_var")
  adlb <- flag_variables(adlb, FALSE, TRUE, TRUE) %>% dplyr::rename(WGRHIFL = "new_var")
  adlb <- flag_variables(adlb, FALSE, FALSE, TRUE) %>% dplyr::rename(WGRLOFL = "new_var")
  adlb <- flag_variables(adlb, TRUE, TRUE, TRUE) %>% dplyr::rename(WGRHIVFL = "new_var")
  adlb <- flag_variables(adlb, TRUE, FALSE, TRUE) %>% dplyr::rename(WGRLOVFL = "new_var")

  tmc_ex_adlb <- adlb %>% dplyr::mutate(
    ANL01FL = ifelse(
      (.data$ABLFL == "Y" | (.data$WORS01FL == "Y" & is.na(.data$DTYPE))) &
        (.data$AVISIT != "SCREENING"),
      "Y",
      ""
    ),
    PARAM = as.factor(.data$PARAM)
  )

  # BNRIND column
  tmc_ex_adlb <- tmc_ex_adlb %>%
    group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    mutate(BNRIND = .data$ANRIND[.data$ABLFL == "Y"]) %>%
    ungroup()

  # ADY column
  tmc_ex_adlb <- tmc_ex_adlb %>%
    dplyr::mutate(ADY = ceiling(as.numeric(difftime(.data$ADTM, .data$TRTSDTM, units = "days"))))

  # PARAMCD should be factor
  tmc_ex_adlb$PARAMCD <- as.factor(tmc_ex_adlb$PARAMCD)

  # CHG and PCHG columns
  tmc_ex_adlb <- tmc_ex_adlb %>%
    dplyr::mutate(CHG = .data$AVAL - .data$BASE) %>%
    dplyr::mutate(PCHG = 100 * (.data$CHG / .data$BASE))

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adlb")
  formatters::var_labels(tmc_ex_adlb) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adlb)])
  rm(tmp_dt)

  save(tmc_ex_adlb, file = "data/tmc_ex_adlb.rda", compress = "xz")
}
```

## ADMH

```{r admh, eval=FALSE}
generate_admh <- function(adsl = tmc_ex_adsl,
                          max_n_mhs = 10L) {
  set.seed(1)
  lookup_mh <- tibble::tribble(
    ~MHBODSYS, ~MHDECOD, ~MHSOC,
    "cl A", "trm A_1/2", "cl A",
    "cl A", "trm A_2/2", "cl A",
    "cl B", "trm B_1/3", "cl B",
    "cl B", "trm B_2/3", "cl B",
    "cl B", "trm B_3/3", "cl B",
    "cl C", "trm C_1/2", "cl C",
    "cl C", "trm C_2/2", "cl C",
    "cl D", "trm D_1/3", "cl D",
    "cl D", "trm D_2/3", "cl D",
    "cl D", "trm D_3/3", "cl D"
  )

  admh <- Map(
    function(id, sid) {
      n_mhs <- sample(0:max_n_mhs, 1)
      i <- sample(seq_len(nrow(lookup_mh)), n_mhs, TRUE)
      dplyr::mutate(
        lookup_mh[i, ],
        USUBJID = id,
        STUDYID = sid
      )
    },
    adsl$USUBJID,
    adsl$STUDYID
  ) %>%
    Reduce(rbind, .) %>%
    `[`(c(4, 5, 1, 2, 3)) %>%
    dplyr::mutate(MHTERM = .data$MHDECOD)

  admh <- dplyr::inner_join(
    adsl,
    admh,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(.data$TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(.data$TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ASTDTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM, .data$MHTERM) %>%
    dplyr::mutate(MHDISTAT = sample(
      x = c("Resolved", "Ongoing with treatment", "Ongoing without treatment"),
      prob = c(0.6, 0.2, 0.2),
      size = dplyr::n(),
      replace = TRUE
    ))

  tmc_ex_admh <- admh %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(MHSEQ = seq_len(dplyr::n())) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM) %>%
    var_relabel(
      MHBODSYS = "Body System or Organ Class",
      MHDECOD = "Dictionary-Derived Term",
      MHSOC = "Primary System Organ Class",
      MHTERM = "Reported Term for the Medical History",
      MHDISTAT = "Status of Disease",
      MHSEQ = "Sponsor-Defined Identifier"
    )
  
  common_lbls_ind <- sapply(
    names(var_labels(tmc_ex_admh)[is.na(var_labels(tmc_ex_admh))]), function(x) which(names(common_var_labels) == x)
  )
  var_labels(tmc_ex_admh[names(common_lbls_ind)]) <- common_var_labels[common_lbls_ind]

  save(tmc_ex_admh, file = "data/tmc_ex_admh.rda", compress = "xz")
}
```

## ADQS

```{r adqs, eval=FALSE}
generate_adqs <- function(adsl = tmc_ex_adsl,
                          n_assessments = 5L,
                          n_days = 5L) {
  set.seed(1)
  param <- c(
    "BFI All Questions",
    "Fatigue Interference",
    "Function/Well-Being (GF1,GF3,GF7)",
    "Treatment Side Effects (GP2,C5,GP5)",
    "FKSI-19 All Questions"
  )
  paramcd <- c("BFIALL", "FATIGI", "FKSI-FWB", "FKSI-TSE", "FKSIALL")
  visit_format <- "WEEK"

  param_init_list <- relvar_init(param, paramcd)

  adqs <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = param_init_list$relvar1,
    AVISIT = visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days),
    stringsAsFactors = FALSE
  )

  adqs <- dplyr::mutate(
    adqs,
    AVISITN = dplyr::case_when(
      AVISIT == "SCREENING" ~ -1,
      AVISIT == "BASELINE" ~ 0,
      (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
      TRUE ~ NA_real_
    )
  )

  adqs$PARAMCD <- rel_var(df = adqs, var_name = "PARAMCD", var_values = param_init_list$relvar2, related_var = "PARAM")
  adqs$AVAL <- stats::rnorm(nrow(adqs), mean = 50, sd = 8) + adqs$AVISITN * stats::rnorm(nrow(adqs), mean = 5, sd = 2)
  adqs <- adqs[order(adqs$STUDYID, adqs$USUBJID, adqs$PARAMCD, adqs$AVISITN), ]

  adqs <- Reduce(
    rbind,
    lapply(
      split(adqs, adqs$USUBJID),
      function(x) {
        x$STUDYID <- adsl$STUDYID[which(adsl$USUBJID == x$USUBJID[1])]
        x$ABLFL2 <- ifelse(x$AVISIT == "SCREENING", "Y", "")
        x$ABLFL <- ifelse(
          toupper(visit_format) == "WEEK" & x$AVISIT == "BASELINE",
          "Y",
          ifelse(
            toupper(visit_format) == "CYCLE" & x$AVISIT == "CYCLE 1 DAY 1",
            "Y",
            ""
          )
        )
        x
      }
    )
  )

  adqs$BASE <- ifelse(adqs$ABLFL2 != "Y", retain(adqs, adqs$AVAL, adqs$ABLFL == "Y"), NA)
  adqs <- adqs %>% dplyr::mutate(CHG = .data$AVAL - .data$BASE)

  adqs <- dplyr::inner_join(
    adsl,
    adqs,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ADTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  tmc_ex_adqs <- adqs %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$AVISITN,
      .data$ADTM
    )

  common_lbls_ind <- sapply(
    names(var_labels(tmc_ex_adqs)[is.na(var_labels(tmc_ex_adqs))]), function(x) which(names(common_var_labels) == x)
  )
  var_labels(tmc_ex_adqs[names(common_lbls_ind)]) <- common_var_labels[common_lbls_ind]

  save(tmc_ex_adqs, file = "data/tmc_ex_adqs.rda", compress = "xz")
}
```

## ADRS

```{r adrs, eval=FALSE}
generate_adrs <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  param_codes <- stats::setNames(1:5, c("CR", "PR", "SD", "PD", "NE"))

  lookup_ars <- expand.grid(
    ARM = c("A: Drug X", "B: Placebo", "C: Combination"),
    AVALC = names(param_codes)
  ) %>% dplyr::mutate(
    AVAL = param_codes[.data$AVALC],
    p_scr = c(rep(0, 3), rep(0, 3), c(1, 1, 1), c(0, 0, 0), c(0, 0, 0)),
    p_bsl = c(rep(0, 3), rep(0, 3), c(1, 1, 1), c(0, 0, 0), c(0, 0, 0)),
    p_cycle = c(c(.4, .3, .5), c(.35, .25, .25), c(.1, .2, .08), c(.14, 0.15, 0.15), c(.01, 0.1, 0.02)),
    p_eoi = c(c(.4, .3, .5), c(.35, .25, .25), c(.1, .2, .08), c(.14, 0.15, 0.15), c(.01, 0.1, 0.02)),
    p_fu = c(c(.3, .2, .4), c(.2, .1, .3), c(.2, .2, .2), c(.3, .5, 0.1), rep(0, 3))
  )

  adrs <- split(adsl, adsl$USUBJID) %>%
    lapply(function(pinfo) {
      probs <- dplyr::filter(lookup_ars, .data$ARM == as.character(pinfo$ACTARM))

      # screening
      rsp_screen <- sample(probs$AVALC, 1, prob = probs$p_scr) %>% as.character()
      # baseline
      rsp_bsl <- sample(probs$AVALC, 1, prob = probs$p_bsl) %>% as.character()
      # cycle
      rsp_c2d1 <- sample(probs$AVALC, 1, prob = probs$p_cycle) %>% as.character()
      rsp_c4d1 <- sample(probs$AVALC, 1, prob = probs$p_cycle) %>% as.character()
      # end of induction
      rsp_eoi <- sample(probs$AVALC, 1, prob = probs$p_eoi) %>% as.character()
      # follow up
      rsp_fu <- sample(probs$AVALC, 1, prob = probs$p_fu) %>% as.character()

      best_rsp <- min(param_codes[c(rsp_screen, rsp_bsl, rsp_eoi, rsp_fu, rsp_c2d1, rsp_c4d1)])
      best_rsp_i <- which.min(param_codes[c(rsp_screen, rsp_bsl, rsp_eoi, rsp_fu, rsp_c2d1, rsp_c4d1)])

      avisit <- c("SCREENING", "BASELINE", "CYCLE 2 DAY 1", "CYCLE 4 DAY 1", "END OF INDUCTION", "FOLLOW UP")

      # meaningful date information
      trtsdt_int <- as.numeric(as.Date(pinfo$TRTSDTM))
      trtedt_int <- ifelse(
        !is.na(pinfo$TRTEDTM), as.numeric(as.Date(pinfo$TRTEDTM)),
        floor(trtsdt_int + study_duration_secs / 86400)
      )
      scr_date <- as.POSIXct(((trtsdt_int - 100) * 86400), origin = "1970-01-01")
      bs_date <- pinfo$TRTSDTM
      flu_date <- as.POSIXct((sample(trtsdt_int:trtedt_int, size = 1) * 86400), origin = "1970-01-01")
      eoi_date <- as.POSIXct((sample(trtsdt_int:trtedt_int, size = 1) * 86400), origin = "1970-01-01")
      c2d1_date <- as.POSIXct((sample(trtsdt_int:trtedt_int, size = 1) * 86400), origin = "1970-01-01")
      c4d1_date <- min(c2d1_date + 60 * 86400, pinfo$TRTEDTM)

      tibble::tibble(
        STUDYID = pinfo$STUDYID,
        USUBJID = pinfo$USUBJID,
        PARAMCD = as.factor(c(rep("OVRINV", 6), "BESRSPI", "INVET")),
        PARAM = as.factor(dplyr::recode(
          .data$PARAMCD,
          OVRINV = "Overall Response by Investigator - by visit",
          OVRSPI = "Best Overall Response by Investigator (no confirmation required)",
          BESRSPI = "Best Confirmed Overall Response by Investigator",
          INVET = "Investigator End Of Induction Response"
        )),
        AVALC = c(
          rsp_screen, rsp_bsl, rsp_c2d1, rsp_c4d1, rsp_eoi, rsp_fu,
          names(param_codes)[best_rsp],
          rsp_eoi
        ),
        AVAL = param_codes[.data$AVALC],
        AVISIT = factor(c(avisit, avisit[best_rsp_i], avisit[5]), levels = avisit)
      ) %>%
        merge(
          tibble::tibble(
            AVISIT = avisit,
            ADTM = c(scr_date, bs_date, c2d1_date, c4d1_date, eoi_date, flu_date),
            AVISITN = c(-1, 0, 2, 4, 999, 999),
            TRTSDTM = pinfo$TRTSDTM
          ) %>%
            dplyr::select(-"TRTSDTM"),
          by = "AVISIT"
        )
    }) %>%
    Reduce(rbind, .) %>%
    dplyr::mutate(
      AVALC = factor(.data$AVALC, levels = names(param_codes)),
      DTHFL = factor(sample(c("Y", "N"), nrow(.), replace = TRUE, prob = c(1, 0.8)))
    )

  adrs <- var_relabel(
    adrs,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge ADSL to be able to add RS date and study day variables
  adrs <- dplyr::inner_join(
    adsl,
    adrs,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  )

  tmc_ex_adrs <- adrs %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$AVISITN,
      .data$ADTM
    )

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adrs")
  formatters::var_labels(tmc_ex_adrs) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adrs)])
  rm(tmp_dt)

  save(tmc_ex_adrs, file = "data/tmc_ex_adrs.rda", compress = "xz")
}
```

## ADTTE

```{r adtte, eval=FALSE}
generate_adtte <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  lookup_tte <- tibble::tribble(
    ~ARM, ~PARAMCD, ~PARAM, ~LAMBDA, ~CNSR_P,
    "ARM A", "OS", "Overall Survival", log(2) / 610, 0.4,
    "ARM B", "OS", "Overall Survival", log(2) / 490, 0.3,
    "ARM C", "OS", "Overall Survival", log(2) / 365, 0.2,
    "ARM A", "PFS", "Progression Free Survival", log(2) / 365, 0.4,
    "ARM B", "PFS", "Progression Free Survival", log(2) / 305, 0.3,
    "ARM C", "PFS", "Progression Free Survival", log(2) / 243, 0.2,
    "ARM A", "EFS", "Event Free Survival", log(2) / 365, 0.4,
    "ARM B", "EFS", "Event Free Survival", log(2) / 305, 0.3,
    "ARM C", "EFS", "Event Free Survival", log(2) / 243, 0.2,
    "ARM A", "CRSD", "Duration of Confirmed Response", log(2) / 305, 0.4,
    "ARM B", "CRSD", "Duration of Confirmed Response", log(2) / 243, 0.3,
    "ARM C", "CRSD", "Duration of Confirmed Response", log(2) / 182, 0.2
  )

  evntdescr_sel <- c(
    "Death",
    "Disease Progression",
    "Last Tumor Assessment",
    "Adverse Event",
    "Last Date Known To Be Alive"
  )

  cnsdtdscr_sel <- c(
    "Preferred Term",
    "Clinical Cut Off",
    "Completion or Discontinuation",
    "End of AE Reporting Period"
  )

  adtte <- split(adsl, adsl$USUBJID) %>%
    lapply(FUN = function(pinfo) {
      lookup_tte %>%
        dplyr::filter(.data$ARM == as.character(pinfo$ACTARMCD)) %>%
        dplyr::rowwise() %>%
        dplyr::mutate(
          STUDYID = pinfo$STUDYID,
          USUBJID = pinfo$USUBJID,
          CNSR = sample(c(0, 1), 1, prob = c(1 - .data$CNSR_P, .data$CNSR_P)),
          AVAL = stats::rexp(1, .data$LAMBDA),
          AVALU = "DAYS",
          EVNTDESC = if (.data$CNSR == 1) {
            sample(evntdescr_sel[-c(1:2)], 1)
          } else {
            ifelse(.data$PARAMCD == "OS",
              sample(evntdescr_sel[1], 1),
              sample(evntdescr_sel[c(1:2)], 1)
            )
          }
        ) %>%
        dplyr::select(-"LAMBDA", -"CNSR_P")
    }) %>%
    Reduce(rbind, .)

  adtte <- var_relabel(
    adtte,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge ADSL to be able to add TTE date and study day variables
  adtte <- dplyr::inner_join(
    adsl,
    dplyr::select(adtte, -"ARM"),
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(TRTEDTM)),
      is.na(TRTEDTM) ~ floor(trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ADTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  adtte <- adtte %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(PARAM = as.factor(.data$PARAM)) %>%
    dplyr::mutate(PARAMCD = as.factor(.data$PARAMCD)) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$ADTM
    )

  # adding adverse event counts and log follow-up time
  tmc_ex_adtte <- dplyr::bind_rows(
    adtte,
    data.frame(adtte %>%
      dplyr::group_by(.data$USUBJID) %>%
      dplyr::slice_head(n = 1) %>%
      dplyr::mutate(
        PARAMCD = "TNE",
        PARAM = "Total Number of Exacerbations",
        AVAL = stats::rpois(1, 3),
        AVALU = "COUNT",
        lgTMATRSK = log(stats::rexp(1, rate = 3)),
        dplyr::across(c("ADTM", "EVNTDESC"), ~NA)
      ))
  ) %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$ADTM
    )

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adtte")
  formatters::var_labels(tmc_ex_adtte) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adtte)])
  rm(tmp_dt)

  save(tmc_ex_adtte, file = "data/tmc_ex_adtte.rda", compress = "xz")
}
```

## ADVS

```{r advs, eval=FALSE}
generate_advs <- function(adsl = tmc_ex_adsl,
                          n_assessments = 5L,
                          n_days = 5L) {
  set.seed(1)
  param <- c(
    "Diastolic Blood Pressure",
    "Pulse Rate",
    "Respiratory Rate",
    "Systolic Blood Pressure",
    "Temperature", "Weight"
  )
  paramcd <- c("DIABP", "PULSE", "RESP", "SYSBP", "TEMP", "WEIGHT")
  paramu <- c("Pa", "beats/min", "breaths/min", "Pa", "C", "Kg")
  visit_format <- "WEEK"

  param_init_list <- relvar_init(param, paramcd)
  unit_init_list <- relvar_init(param, paramu)

  advs <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = as.factor(param_init_list$relvar1),
    AVISIT = visit_schedule(visit_format = visit_format, n_assessments = n_assessments),
    stringsAsFactors = FALSE
  )

  advs <- dplyr::mutate(
    advs,
    AVISITN = dplyr::case_when(
      AVISIT == "SCREENING" ~ -1,
      AVISIT == "BASELINE" ~ 0,
      (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
      TRUE ~ NA_real_
    )
  )

  advs$PARAMCD <- as.factor(rel_var(
    df = advs,
    var_name = "PARAMCD",
    var_values = param_init_list$relvar2,
    related_var = "PARAM"
  ))
  advs$AVALU <- as.factor(rel_var(
    df = advs,
    var_name = "AVALU",
    var_values = unit_init_list$relvar2,
    related_var = "PARAM"
  ))

  advs$AVAL <- stats::rnorm(nrow(advs), mean = 50, sd = 8)
  advs <- advs[order(advs$STUDYID, advs$USUBJID, advs$PARAMCD, advs$AVISITN), ]

  advs <- Reduce(rbind, lapply(split(advs, advs$USUBJID), function(x) {
    x$STUDYID <- adsl$STUDYID[which(adsl$USUBJID == x$USUBJID[1])]
    x$ABLFL2 <- ifelse(x$AVISIT == "SCREENING", "Y", "")
    x$ABLFL <- ifelse(
      toupper(visit_format) == "WEEK" & x$AVISIT == "BASELINE",
      "Y",
      ifelse(
        toupper(visit_format) == "CYCLE" & x$AVISIT == "CYCLE 1 DAY 1",
        "Y",
        ""
      )
    )
    x
  }))

  advs$BASE <- ifelse(advs$ABLFL2 != "Y", retain(advs, advs$AVAL, advs$ABLFL == "Y"), NA)
  advs$BASE2 <- retain(advs, advs$AVAL, advs$ABLFL2 == "Y")

  advs <- advs %>%
    dplyr::mutate(CHG = .data$AVAL - .data$BASE) %>%
    dplyr::mutate(PCHG = 100 * (.data$CHG / .data$BASE)) %>%
    dplyr::mutate(
      ANRIND = c("HIGH", "LOW", "NORMAL") %>%
        sample_fct(nrow(advs), prob = c(0.1, 0.1, 0.8))
    ) %>%
    dplyr::mutate(ANRLO = dplyr::case_when(
      .data$PARAMCD == "DIABP" ~ 80,
      .data$PARAMCD == "PULSE" ~ 60,
      .data$PARAMCD == "RESP" ~ 12,
      .data$PARAMCD == "SYSBP" ~ 120,
      .data$PARAMCD == "TEMP" ~ 36.1,
      .data$PARAMCD == "WEIGHT" ~ 40
    )) %>%
    dplyr::mutate(ANRHI = dplyr::case_when(
      .data$PARAMCD == "DIABP" ~ 120,
      .data$PARAMCD == "PULSE" ~ 100,
      .data$PARAMCD == "RESP" ~ 20,
      .data$PARAMCD == "SYSBP" ~ 180,
      .data$PARAMCD == "TEMP" ~ 37.2,
      .data$PARAMCD == "WEIGHT" ~ 100
    )) %>%
    dplyr::group_by(.data$USUBJID, .data$PARAMCD) %>%
    dplyr::ungroup()

  advs <- dplyr::inner_join(
    adsl,
    advs,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(TRTEDTM)),
      is.na(TRTEDTM) ~ floor(trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(
      ADTM = as.POSIXct(
        (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
        origin = "1970-01-01"
      )
    ) %>%
    dplyr::mutate(ADY = ceiling(as.numeric(difftime(.data$ADTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  tmc_ex_advs <- advs %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$AVISITN,
      .data$ADTM
    )
  
  common_lbls_ind <- sapply(
    names(var_labels(tmc_ex_advs)[is.na(var_labels(tmc_ex_advs))]), function(x) which(names(common_var_labels) == x)
  )
  var_labels(tmc_ex_advs[names(common_lbls_ind)]) <- common_var_labels[common_lbls_ind]
  
  save(tmc_ex_advs, file = "data/tmc_ex_advs.rda", compress = "xz")
}
```

## Generate Data

```{r generate data, eval=FALSE}
# Generate & load adsl
tmp_fol <- getwd()
setwd(dirname(tmp_fol))
generate_adsl()
load("data/tmc_ex_adsl.rda")

# Generate other datasets
generate_adae()
generate_adaette()
generate_adcm()
generate_adeg()
generate_adex()
generate_adlb()
generate_admh()
generate_adqs()
generate_adrs()
generate_adtte()
generate_advs()

setwd(tmp_fol)
```
