---
title: "Example Data Generation"
date: "`r Sys.Date()`"
output:
    rmarkdown::html_document:
        theme: "spacelab"
        highlight: "kate"
        toc: true
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Example Data Generation}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
editor_options:
    markdown: 
        wrap: 72
---

## Generating minimal data to test `teal.modules.clinical`

The following script is used to create and save cached synthetic CDISC data to the `data/` directory to use in examples and tests in the `teal.modules.clinical` package. This script/vignette was initialized by Emily de la Rua in `tern`.

_Disclaimer_: this vignette concerns mainly the development of minimal and stable test data and it is kept internal for feature traceability.

## Setup & Helper Functions

```{r setup, eval=FALSE}
library(dplyr)
library(formatters)

study_duration_secs <- 31556952 * 2

sample_fct <- function(x, N, ...) { # nolint
  checkmate::assert_number(N)
  factor(sample(x, N, replace = TRUE, ...), levels = if (is.factor(x)) levels(x) else x)
}

retain <- function(df, value_var, event, outside = NA) {
  indices <- c(1, which(event == TRUE), nrow(df) + 1)
  values <- c(outside, value_var[event == TRUE])
  rep(values, diff(indices))
}

relvar_init <- function(relvar1, relvar2) {
  if (length(relvar1) != length(relvar2)) {
    message(simpleError(
      "The argument value length of relvar1 and relvar2 differ. They must contain the same number of elements."
    ))
    return(NA)
  }
  return(list("relvar1" = relvar1, "relvar2" = relvar2))
}

rel_var <- function(df = NULL, var_name = NULL, var_values = NULL, related_var = NULL) {
  if (is.null(df)) {
    message("Missing data frame argument value.")
    return(NA)
  } else {
    n_relvar1 <- length(unique(df[, related_var, drop = TRUE]))
    n_relvar2 <- length(var_values)
    if (n_relvar1 != n_relvar2) {
      message(paste("Unequal vector lengths for", related_var, "and", var_name))
      return(NA)
    } else {
      relvar1 <- unique(df[, related_var, drop = TRUE])
      relvar2_values <- rep(NA, nrow(df))
      for (r in seq_len(length(relvar1))) {
        matched <- which(df[, related_var, drop = TRUE] == relvar1[r])
        relvar2_values[matched] <- var_values[r]
      }
      return(relvar2_values)
    }
  }
}

visit_schedule <- function(visit_format = "WEEK",
                           n_assessments = 10L,
                           n_days = 5L) {
  if (!(toupper(visit_format) %in% c("WEEK", "CYCLE"))) {
    message("Visit format value must either be: WEEK or CYCLE")
    return(NA)
  }
  if (toupper(visit_format) == "WEEK") {
    assessments <- 1:n_assessments
    assessments_ord <- -1:n_assessments
    visit_values <- c("SCREENING", "BASELINE", paste(toupper(visit_format), assessments, "DAY", (assessments * 7) + 1))
  } else if (toupper(visit_format) == "CYCLE") {
    cycles <- sort(rep(1:n_assessments, times = 1, each = n_days))
    days <- rep(seq(1:n_days), times = n_assessments, each = 1)
    assessments_ord <- 0:(n_assessments * n_days)
    visit_values <- c("SCREENING", paste(toupper(visit_format), cycles, "DAY", days))
  }
  visit_values <- stats::reorder(factor(visit_values), assessments_ord)
}

## ADSL

generate_adsl <- function(N = 200) { # nolint
  set.seed(1)
  sys_dtm <- as.numeric(strptime("20/2/2019 11:16:16.683", "%d/%m/%Y %H:%M:%OS"))
  country_site_prob <- c(.5, .121, .077, .077, .075, .052, .046, .025, .014, .003)

  tmc_ex_adsl <- tibble::tibble(
    STUDYID = rep("AB12345", N),
    COUNTRY = sample_fct(
      c("CHN", "USA", "BRA", "PAK", "NGA", "RUS", "JPN", "GBR", "CAN", "CHE"),
      N,
      prob = country_site_prob
    ),
    SITEID = sample_fct(1:20, N, prob = rep(country_site_prob, times = 2)),
    SUBJID = paste("id", seq_len(N), sep = "-"),
    AGE = sapply(stats::rchisq(N, df = 5, ncp = 10), max, 0) + 20,
    SEX = c("F", "M") %>% sample_fct(N, prob = c(.52, .48)),
    ARMCD = c("ARM A", "ARM B", "ARM C") %>% sample_fct(N),
    ARM = dplyr::recode(
      .data$ARMCD,
      "ARM A" = "A: Drug X", "ARM B" = "B: Placebo", "ARM C" = "C: Combination"
    ),
    ACTARMCD = .data$ARMCD,
    ACTARM = .data$ARM,
    RACE = c(
      "ASIAN", "BLACK OR AFRICAN AMERICAN", "WHITE", "AMERICAN INDIAN OR ALASKA NATIVE",
      "MULTIPLE", "NATIVE HAWAIIAN OR OTHER PACIFIC ISLANDER", "OTHER", "UNKNOWN"
    ) %>%
      sample_fct(N, prob = c(.55, .23, .16, .05, .004, .003, .002, .002)),
    TRTSDTM = as.POSIXct(
      sys_dtm + sample(seq(0, study_duration_secs), size = N, replace = TRUE),
      origin = "1970-01-01"
    ),
    TRTEDTM = as.POSIXct(as.numeric(.data$TRTSDTM) + study_duration_secs, origin = "1970-01-01"),
    EOSDY = as.numeric(ceiling(difftime(.data$TRTEDTM, .data$TRTSDTM, units = "days"))),
    STRATA1 = c("A", "B", "C") %>% sample_fct(N),
    STRATA2 = c("S1", "S2") %>% sample_fct(N),
    BMRKR1 = stats::rchisq(N, 6),
    BMRKR2 = sample_fct(c("LOW", "MEDIUM", "HIGH"), N)
  )

  # associate sites with countries and regions
  tmc_ex_adsl <- tmc_ex_adsl %>%
    dplyr::mutate(
      SITEID = paste0(.data$COUNTRY, "-", .data$SITEID),
      REGION1 = factor(dplyr::case_when(
        COUNTRY %in% c("NGA") ~ "Africa",
        COUNTRY %in% c("CHN", "JPN", "PAK") ~ "Asia",
        COUNTRY %in% c("RUS") ~ "Eurasia",
        COUNTRY %in% c("GBR") ~ "Europe",
        COUNTRY %in% c("CAN", "USA") ~ "North America",
        COUNTRY %in% c("BRA") ~ "South America",
        TRUE ~ as.character(NA)
      )),
      SAFFL = factor("Y")
    ) %>%
    dplyr::mutate(USUBJID = paste(.data$STUDYID, .data$SITEID, .data$SUBJID, sep = "-"))

  # disposition related variables
  # using probability of 1 for the "DEATH" level to ensure at least one death record exists
  l_dcsreas <- list(
    choices = c(
      "ADVERSE EVENT", "DEATH", "LACK OF EFFICACY", "PHYSICIAN DECISION",
      "PROTOCOL VIOLATION", "WITHDRAWAL BY PARENT/GUARDIAN", "WITHDRAWAL BY SUBJECT"
    ),
    prob = c(.2, 1, .1, .1, .2, .1, .1)
  )
  l_dthcat_other <- list(
    choices = c(
      "Post-study reporting of death", "LOST TO FOLLOW UP", "MISSING", "SUICIDE", "UNKNOWN"
    ),
    prob = c(.1, .3, .3, .2, .1)
  )

  tmc_ex_adsl <- tmc_ex_adsl %>%
    dplyr::mutate(EOSDT = as.Date(.data$TRTEDTM)) %>%
    dplyr::mutate(EOSDY = as.numeric(ceiling(difftime(.data$TRTEDTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::mutate(EOSSTT = dplyr::case_when(
      EOSDY == max(EOSDY, na.rm = TRUE) ~ "COMPLETED",
      EOSDY < max(EOSDY, na.rm = TRUE) ~ "DISCONTINUED",
      is.na(TRTEDTM) ~ "ONGOING"
    )) %>%
    dplyr::mutate(EOTSTT = .data$EOSSTT) %>%
    dplyr::mutate(
      DCSREAS = ifelse(
        .data$EOSSTT == "DISCONTINUED",
        sample(x = l_dcsreas$choices, size = N, replace = TRUE, prob = l_dcsreas$prob),
        as.character(NA)
      )
    ) %>%
    dplyr::mutate(study_duration_secs = study_duration_secs)

  tmc_ex_adsl <- tmc_ex_adsl %>%
    dplyr::mutate(DTHDT = dplyr::case_when(
      DCSREAS == "DEATH" ~ as.Date(.data$TRTEDTM) + sample(0:50, size = N, replace = TRUE)
    ))

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adsl")
  formatters::var_labels(tmc_ex_adsl) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adsl)])
  rm(tmp_dt)

  save(tmc_ex_adsl, file = "data/tmc_ex_adsl.rda", compress = "xz")
}

## ADAE

generate_adae <- function(adsl = tmc_ex_adsl,
                          max_n_aes = 5) {
  set.seed(1)
  lookup_ae <- tibble::tribble(
    ~AEBODSYS, ~AELLT, ~AEDECOD, ~AEHLT, ~AEHLGT, ~AETOXGR, ~AESOC, ~AESER, ~AEREL,
    "cl A.1", "llt A.1.1.1.1", "dcd A.1.1.1.1", "hlt A.1.1.1", "hlgt A.1.1", "1", "cl A", "N", "N",
    "cl A.1", "llt A.1.1.1.2", "dcd A.1.1.1.2", "hlt A.1.1.1", "hlgt A.1.1", "2", "cl A", "Y", "N",
    "cl B.1", "llt B.1.1.1.1", "dcd B.1.1.1.1", "hlt B.1.1.1", "hlgt B.1.1", "5", "cl B", "Y", "Y",
    "cl B.2", "llt B.2.1.2.1", "dcd B.2.1.2.1", "hlt B.2.1.2", "hlgt B.2.1", "3", "cl B", "N", "N",
    "cl B.2", "llt B.2.2.3.1", "dcd B.2.2.3.1", "hlt B.2.2.3", "hlgt B.2.2", "1", "cl B", "Y", "N",
    "cl C.1", "llt C.1.1.1.3", "dcd C.1.1.1.3", "hlt C.1.1.1", "hlgt C.1.1", "4", "cl C", "N", "Y",
    "cl C.2", "llt C.2.1.2.1", "dcd C.2.1.2.1", "hlt C.2.1.2", "hlgt C.2.1", "2", "cl C", "N", "Y",
    "cl D.1", "llt D.1.1.1.1", "dcd D.1.1.1.1", "hlt D.1.1.1", "hlgt D.1.1", "5", "cl D", "Y", "Y",
    "cl D.1", "llt D.1.1.4.2", "dcd D.1.1.4.2", "hlt D.1.1.4", "hlgt D.1.1", "3", "cl D", "N", "N",
    "cl D.2", "llt D.2.1.5.3", "dcd D.2.1.5.3", "hlt D.2.1.5", "hlgt D.2.1", "1", "cl D", "N", "Y"
  )

  aag <- utils::read.table(
    sep = ",", header = TRUE,
    text = paste(
      "NAMVAR,SRCVAR,GRPTYPE,REFNAME,REFTERM,SCOPE",
      "CQ01NAM,AEDECOD,CUSTOM,D.2.1.5.3/A.1.1.1.1 aesi,dcd D.2.1.5.3,",
      "CQ01NAM,AEDECOD,CUSTOM,D.2.1.5.3/A.1.1.1.1 aesi,dcd A.1.1.1.1,",
      "SMQ01NAM,AEDECOD,SMQ,C.1.1.1.3/B.2.2.3.1 aesi,dcd C.1.1.1.3,BROAD",
      "SMQ01NAM,AEDECOD,SMQ,C.1.1.1.3/B.2.2.3.1 aesi,dcd B.2.2.3.1,BROAD",
      "SMQ02NAM,AEDECOD,SMQ,Y.9.9.9.9/Z.9.9.9.9 aesi,dcd Y.9.9.9.9,NARROW",
      "SMQ02NAM,AEDECOD,SMQ,Y.9.9.9.9/Z.9.9.9.9 aesi,dcd Z.9.9.9.9,NARROW",
      sep = "\n"
    ), stringsAsFactors = FALSE
  )

  adae <- Map(
    function(id, sid) {
      n_aes <- sample(c(0, seq_len(max_n_aes)), 1)
      i <- sample(seq_len(nrow(lookup_ae)), n_aes, TRUE)
      dplyr::mutate(
        lookup_ae[i, ],
        USUBJID = id,
        STUDYID = sid
      )
    },
    adsl$USUBJID,
    adsl$STUDYID
  ) %>%
    Reduce(rbind, .) %>%
    `[`(c(10, 11, 1, 2, 3, 4, 5, 6, 7, 8, 9)) %>%
    dplyr::mutate(AETERM = gsub("dcd", "trm", .data$AEDECOD)) %>%
    dplyr::mutate(AESEV = dplyr::case_when(
      AETOXGR == 1 ~ "MILD",
      AETOXGR %in% c(2, 3) ~ "MODERATE",
      AETOXGR %in% c(4, 5) ~ "SEVERE"
    ))

  adae <- var_relabel(
    adae,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge adsl to be able to add AE date and study day variables
  adae <- dplyr::inner_join(adae, adsl, by = c("STUDYID", "USUBJID"), multiple = "all") %>% # nolint
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(.data$TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(.data$TRTEDTM) ~ floor(trtsdt_int + (study_duration_secs) / 86400)
    )) %>%
    dplyr::mutate(ASTDTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(astdt_int = as.numeric(as.Date(.data$ASTDTM))) %>%
    dplyr::mutate(ASTDY = ceiling(as.numeric(difftime(.data$ASTDTM, .data$TRTSDTM, units = "days")))) %>%
    # add 1 to end of range incase both values passed to sample() are the same
    dplyr::mutate(AENDTM = as.POSIXct(
      (sample(.data$astdt_int:(.data$trtedt_int + 1), size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(AENDY = ceiling(as.numeric(difftime(.data$AENDTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::mutate(LDOSEDTM = as.POSIXct(
      ifelse(.data$TRTSDTM < .data$ASTDTM,
        lubridate::as_datetime(stats::runif(1, .data$TRTSDTM, .data$ASTDTM), tz = "EST"),
        .data$ASTDTM
      ),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int", -"astdt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM, .data$AETERM)

  adae <- adae %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(AESEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$AESEQ) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$ASTDTM,
      .data$AETERM,
      .data$AESEQ
    )

  outcomes <- c(
    "UNKNOWN",
    "NOT RECOVERED/NOT RESOLVED",
    "RECOVERED/RESOLVED WITH SEQUELAE",
    "RECOVERING/RESOLVING",
    "RECOVERED/RESOLVED"
  )

  adae <- adae %>%
    dplyr::mutate(AEOUT = factor(ifelse(
      .data$AETOXGR == "5",
      "FATAL",
      as.character(sample_fct(outcomes, nrow(adae), prob = c(0.1, 0.2, 0.1, 0.3, 0.3)))
    ))) %>%
    dplyr::mutate(TRTEMFL = ifelse(.data$ASTDTM >= .data$TRTSDTM, "Y", ""))

  l_aag <- split(aag, interaction(aag$NAMVAR, aag$SRCVAR, aag$GRPTYPE, drop = TRUE))

  # Create aesi flags
  l_aesi <- lapply(l_aag, function(d_adag, d_adae) {
    names(d_adag)[names(d_adag) == "REFTERM"] <- d_adag$SRCVAR[1]
    names(d_adag)[names(d_adag) == "REFNAME"] <- d_adag$NAMVAR[1]

    if (d_adag$GRPTYPE[1] == "CUSTOM") {
      d_adag <- d_adag[-which(names(d_adag) == "SCOPE")]
    } else if (d_adag$GRPTYPE[1] == "SMQ") {
      names(d_adag)[names(d_adag) == "SCOPE"] <- paste0(substr(d_adag$NAMVAR[1], 1, 5), "SC")
    }

    d_adag <- d_adag[-which(names(d_adag) %in% c("NAMVAR", "SRCVAR", "GRPTYPE"))]
    d_new <- dplyr::left_join(x = d_adae, y = d_adag, by = intersect(names(d_adae), names(d_adag)))
    d_new[, dplyr::setdiff(names(d_new), names(d_adae)), drop = FALSE]
  }, adae)

  tmc_ex_adae <- dplyr::bind_cols(adae, l_aesi)

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adae")
  formatters::var_labels(tmc_ex_adae) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adae)])
  rm(tmp_dt)

  save(tmc_ex_adae, file = "data/tmc_ex_adae.rda", compress = "xz")
}

## ADLB

generate_adlb <- function(adsl = tmc_ex_adsl,
                          max_n_lbs = 5L) {
  set.seed(1)
  lbcat <- c("CHEMISTRY", "CHEMISTRY", "IMMUNOLOGY")
  param <- c(
    "Alanine Aminotransferase Measurement",
    "C-Reactive Protein Measurement",
    "Immunoglobulin A Measurement"
  )
  paramcd <- c("ALT", "CRP", "IGA")
  paramu <- c("U/L", "mg/L", "g/L")
  aval_mean <- c(20, 1, 2)
  visit_format <- "WEEK"
  n_assessments <- 5L
  n_days <- 5L

  # validate and initialize related variables
  lbcat_init_list <- relvar_init(param, lbcat)
  param_init_list <- relvar_init(param, paramcd)
  unit_init_list <- relvar_init(param, paramu)

  adlb <- expand.grid(
    STUDYID = unique(adsl$STUDYID),
    USUBJID = adsl$USUBJID,
    PARAM = as.factor(param_init_list$relvar1),
    AVISIT = visit_schedule(visit_format = visit_format, n_assessments = n_assessments, n_days = n_days),
    stringsAsFactors = FALSE
  )

  # assign AVAL based on different test
  adlb <- adlb %>%
    dplyr::mutate(AVAL = stats::rnorm(nrow(adlb), mean = 1, sd = 0.2)) %>%
    dplyr::left_join(data.frame(PARAM = param, ADJUST = aval_mean), by = "PARAM") %>%
    dplyr::mutate(AVAL = .data$AVAL * .data$ADJUST) %>%
    dplyr::select(-"ADJUST")

  # assign related variable values: PARAMxLBCAT are related
  adlb$LBCAT <- as.factor(rel_var(
    df = adlb,
    var_name = "LBCAT",
    var_values = lbcat_init_list$relvar2,
    related_var = "PARAM"
  ))

  # assign related variable values: PARAMxPARAMCD are related
  adlb$PARAMCD <- as.factor(rel_var(
    df = adlb,
    var_name = "PARAMCD",
    var_values = param_init_list$relvar2,
    related_var = "PARAM"
  ))

  adlb$AVALU <- as.factor(rel_var(
    df = adlb,
    var_name = "AVALU",
    var_values = unit_init_list$relvar2,
    related_var = "PARAM"
  ))

  adlb <- adlb %>% dplyr::mutate(AVISITN = dplyr::case_when(
    AVISIT == "SCREENING" ~ -1,
    AVISIT == "BASELINE" ~ 0,
    (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
    TRUE ~ NA_real_
  ))

  adlb <- adlb %>%
    dplyr::mutate(AVISITN = dplyr::case_when(
      AVISIT == "SCREENING" ~ -1,
      AVISIT == "BASELINE" ~ 0,
      (grepl("^WEEK", AVISIT) | grepl("^CYCLE", AVISIT)) ~ as.numeric(AVISIT) - 2,
      TRUE ~ NA_real_
    ))

  # order to prepare for change from screening and baseline values
  adlb <- adlb[order(adlb$STUDYID, adlb$USUBJID, adlb$PARAMCD, adlb$AVISITN), ]

  adlb <- Reduce(rbind, lapply(split(adlb, adlb$USUBJID), function(x) {
    x$STUDYID <- adsl$STUDYID[which(adsl$USUBJID == x$USUBJID[1])]
    x$ABLFL2 <- ifelse(x$AVISIT == "SCREENING", "Y", "")
    x$ABLFL <- ifelse(toupper(visit_format) == "WEEK" & x$AVISIT == "BASELINE",
      "Y",
      ifelse(toupper(visit_format) == "CYCLE" & x$AVISIT == "CYCLE 1 DAY 1", "Y", "")
    )
    x
  }))

  adlb$BASE <- ifelse(adlb$ABLFL2 != "Y", retain(adlb, adlb$AVAL, adlb$ABLFL == "Y"), NA)

  anrind_choices <- c("HIGH", "LOW", "NORMAL")

  adlb <- adlb %>%
    dplyr::mutate(BASETYPE = "LAST") %>%
    dplyr::mutate(ANRIND = sample_fct(anrind_choices, nrow(adlb), prob = c(0.1, 0.1, 0.8))) %>%
    dplyr::mutate(ANRLO = dplyr::case_when(
      .data$PARAMCD == "ALT" ~ 7,
      .data$PARAMCD == "CRP" ~ 8,
      .data$PARAMCD == "IGA" ~ 0.8
    )) %>%
    dplyr::mutate(ANRHI = dplyr::case_when(
      .data$PARAMCD == "ALT" ~ 55,
      .data$PARAMCD == "CRP" ~ 10,
      .data$PARAMCD == "IGA" ~ 3
    )) %>%
    dplyr::mutate(DTYPE = NA) %>%
    dplyr::mutate(ATOXGR = factor(dplyr::case_when(
      .data$ANRIND == "LOW" ~ sample(
        c("-1", "-2", "-3", "-4", "-5"),
        nrow(adlb),
        replace = TRUE,
        prob = c(0.30, 0.25, 0.20, 0.15, 0)
      ),
      .data$ANRIND == "HIGH" ~ sample(
        c("1", "2", "3", "4", "5"),
        nrow(adlb),
        replace = TRUE,
        prob = c(0.30, 0.25, 0.20, 0.15, 0)
      ),
      .data$ANRIND == "NORMAL" ~ "0"
    ))) %>%
    dplyr::group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    dplyr::mutate(BTOXGR = .data$ATOXGR[.data$ABLFL == "Y"]) %>%
    dplyr::ungroup()

  # High and low descriptions of the different PARAMCD values
  # This is currently hard coded as the GDSR does not have these descriptions yet
  grade_lookup <- tibble::tribble(
    ~PARAMCD, ~ATOXDSCL, ~ATOXDSCH,
    "ALB", "Hypoalbuminemia", NA_character_,
    "ALKPH", NA_character_, "Alkaline phosphatase increased",
    "ALT", NA_character_, "Alanine aminotransferase increased",
    "AST", NA_character_, "Aspartate aminotransferase increased",
    "BILI", NA_character_, "Blood bilirubin increased",
    "CA", "Hypocalcemia", "Hypercalcemia",
    "CHOLES", NA_character_, "Cholesterol high",
    "CK", NA_character_, "CPK increased",
    "CREAT", NA_character_, "Creatinine increased",
    "CRP", NA_character_, "C reactive protein increased",
    "GGT", NA_character_, "GGT increased",
    "GLUC", "Hypoglycemia", "Hyperglycemia",
    "HGB", "Anemia", "Hemoglobin increased",
    "IGA", NA_character_, "Immunoglobulin A increased",
    "POTAS", "Hypokalemia", "Hyperkalemia",
    "LYMPH", "CD4 lymphocytes decreased", NA_character_,
    "PHOS", "Hypophosphatemia", NA_character_,
    "PLAT", "Platelet count decreased", NA_character_,
    "SODIUM", "Hyponatremia", "Hypernatremia",
    "WBC", "White blood cell decreased", "Leukocytosis",
  )

  # merge grade_lookup onto adlb
  adlb <- dplyr::left_join(adlb, grade_lookup, by = "PARAMCD")

  adlb <- var_relabel(
    adlb,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge adsl to be able to add LB date and study day variables
  adlb <- dplyr::inner_join(
    adsl,
    adlb,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + study_duration_secs / 86400)
    )) %>%
    dplyr::mutate(ADTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  adlb <- adlb %>%
    dplyr::mutate(ASPID = sample(seq_len(dplyr::n()))) %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(LBSEQ = seq_len(dplyr::n())) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$BASETYPE,
      .data$AVISITN,
      .data$DTYPE,
      .data$ADTM,
      .data$LBSEQ,
      .data$ASPID
    )

  adlb <- adlb %>% dplyr::mutate(ONTRTFL = factor(dplyr::case_when(
    is.na(.data$TRTSDTM) ~ "",
    is.na(.data$ADTM) ~ "Y",
    (.data$ADTM < .data$TRTSDTM) ~ "",
    (.data$ADTM > .data$TRTEDTM) ~ "",
    TRUE ~ "Y"
  )))

  flag_variables <- function(data,
                             apply_grouping,
                             apply_filter,
                             apply_mutate) {
    data_compare <- data %>%
      dplyr::mutate(row_check = seq_len(nrow(data)))

    data <- data_compare %>%
      {
        if (apply_grouping == TRUE) {
          dplyr::group_by(., .data$USUBJID, .data$PARAMCD, .data$BASETYPE, .data$AVISIT)
        } else {
          dplyr::group_by(., .data$USUBJID, .data$PARAMCD, .data$BASETYPE)
        }
      } %>%
      dplyr::arrange(.data$ADTM, .data$ASPID, .data$LBSEQ) %>%
      {
        if (apply_filter == TRUE) {
          dplyr::filter(
            .,
            (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
              (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
          ) %>%
            dplyr::filter(.data$ATOXGR == max(as.numeric(as.character(.data$ATOXGR))))
        } else if (apply_filter == FALSE) {
          dplyr::filter(
            .,
            (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
              (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
          ) %>%
            dplyr::filter(.data$ATOXGR == min(as.numeric(as.character(.data$ATOXGR))))
        } else {
          dplyr::filter(
            .,
            .data$AVAL == min(.data$AVAL) &
              (.data$AVISIT != "BASELINE" & .data$AVISIT != "SCREENING") &
              (.data$ONTRTFL == "Y" | .data$ADTM <= .data$TRTSDTM)
          )
        }
      } %>%
      dplyr::slice(1) %>%
      {
        if (apply_mutate == TRUE) {
          dplyr::mutate(., new_var = ifelse(is.na(.data$DTYPE), "Y", ""))
        } else {
          dplyr::mutate(., new_var = ifelse(is.na(.data$AVAL) == FALSE & is.na(.data$DTYPE), "Y", ""))
        }
      } %>%
      dplyr::ungroup()

    data_compare$new_var <- ifelse(data_compare$row_check %in% data$row_check, "Y", "")

    data_compare <- data_compare[, -which(names(data_compare) %in% c("row_check"))]

    return(data_compare)
  }

  adlb <- flag_variables(adlb, TRUE, "ELSE", FALSE) %>% dplyr::rename(WORS01FL = "new_var")
  adlb <- flag_variables(adlb, FALSE, TRUE, TRUE) %>% dplyr::rename(WGRHIFL = "new_var")
  adlb <- flag_variables(adlb, FALSE, FALSE, TRUE) %>% dplyr::rename(WGRLOFL = "new_var")
  adlb <- flag_variables(adlb, TRUE, TRUE, TRUE) %>% dplyr::rename(WGRHIVFL = "new_var")
  adlb <- flag_variables(adlb, TRUE, FALSE, TRUE) %>% dplyr::rename(WGRLOVFL = "new_var")

  tmc_ex_adlb <- adlb %>% dplyr::mutate(
    ANL01FL = ifelse(
      (.data$ABLFL == "Y" | (.data$WORS01FL == "Y" & is.na(.data$DTYPE))) &
        (.data$AVISIT != "SCREENING"),
      "Y",
      ""
    ),
    PARAM = as.factor(.data$PARAM)
  )

  # BNRIND column
  tmc_ex_adlb <- tmc_ex_adlb %>%
    group_by(.data$USUBJID, .data$PARAMCD, .data$BASETYPE) %>%
    mutate(BNRIND = .data$ANRIND[.data$ABLFL == "Y"]) %>%
    ungroup()

  # ADY column
  tmc_ex_adlb <- tmc_ex_adlb %>%
    dplyr::mutate(ADY = ceiling(as.numeric(difftime(.data$ADTM, .data$TRTSDTM, units = "days"))))

  # PARAMCD should be factor
  tmc_ex_adlb$PARAMCD <- as.factor(tmc_ex_adlb$PARAMCD)

  # CHG and PCHG columns
  tmc_ex_adlb <- tmc_ex_adlb %>%
    dplyr::mutate(CHG = .data$AVAL - .data$BASE) %>%
    dplyr::mutate(PCHG = 100 * (.data$CHG / .data$BASE))

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adlb")
  formatters::var_labels(tmc_ex_adlb) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adlb)])
  rm(tmp_dt)

  save(tmc_ex_adlb, file = "data/tmc_ex_adlb.rda", compress = "xz")
}

## ADRS

generate_adrs <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  param_codes <- stats::setNames(1:5, c("CR", "PR", "SD", "PD", "NE"))

  lookup_ars <- expand.grid(
    ARM = c("A: Drug X", "B: Placebo", "C: Combination"),
    AVALC = names(param_codes)
  ) %>% dplyr::mutate(
    AVAL = param_codes[.data$AVALC],
    p_scr = c(rep(0, 3), rep(0, 3), c(1, 1, 1), c(0, 0, 0), c(0, 0, 0)),
    p_bsl = c(rep(0, 3), rep(0, 3), c(1, 1, 1), c(0, 0, 0), c(0, 0, 0)),
    p_cycle = c(c(.4, .3, .5), c(.35, .25, .25), c(.1, .2, .08), c(.14, 0.15, 0.15), c(.01, 0.1, 0.02)),
    p_eoi = c(c(.4, .3, .5), c(.35, .25, .25), c(.1, .2, .08), c(.14, 0.15, 0.15), c(.01, 0.1, 0.02)),
    p_fu = c(c(.3, .2, .4), c(.2, .1, .3), c(.2, .2, .2), c(.3, .5, 0.1), rep(0, 3))
  )

  adrs <- split(adsl, adsl$USUBJID) %>%
    lapply(function(pinfo) {
      probs <- dplyr::filter(lookup_ars, .data$ARM == as.character(pinfo$ACTARM))

      # screening
      rsp_screen <- sample(probs$AVALC, 1, prob = probs$p_scr) %>% as.character()
      # baseline
      rsp_bsl <- sample(probs$AVALC, 1, prob = probs$p_bsl) %>% as.character()
      # cycle
      rsp_c2d1 <- sample(probs$AVALC, 1, prob = probs$p_cycle) %>% as.character()
      rsp_c4d1 <- sample(probs$AVALC, 1, prob = probs$p_cycle) %>% as.character()
      # end of induction
      rsp_eoi <- sample(probs$AVALC, 1, prob = probs$p_eoi) %>% as.character()
      # follow up
      rsp_fu <- sample(probs$AVALC, 1, prob = probs$p_fu) %>% as.character()

      best_rsp <- min(param_codes[c(rsp_screen, rsp_bsl, rsp_eoi, rsp_fu, rsp_c2d1, rsp_c4d1)])
      best_rsp_i <- which.min(param_codes[c(rsp_screen, rsp_bsl, rsp_eoi, rsp_fu, rsp_c2d1, rsp_c4d1)])

      avisit <- c("SCREENING", "BASELINE", "CYCLE 2 DAY 1", "CYCLE 4 DAY 1", "END OF INDUCTION", "FOLLOW UP")

      # meaningful date information
      trtsdt_int <- as.numeric(as.Date(pinfo$TRTSDTM))
      trtedt_int <- ifelse(
        !is.na(pinfo$TRTEDTM), as.numeric(as.Date(pinfo$TRTEDTM)),
        floor(trtsdt_int + (pinfo$study_duration_secs) / 86400)
      )
      scr_date <- as.POSIXct(((trtsdt_int - 100) * 86400), origin = "1970-01-01")
      bs_date <- pinfo$TRTSDTM
      flu_date <- as.POSIXct((sample(trtsdt_int:trtedt_int, size = 1) * 86400), origin = "1970-01-01")
      eoi_date <- as.POSIXct((sample(trtsdt_int:trtedt_int, size = 1) * 86400), origin = "1970-01-01")
      c2d1_date <- as.POSIXct((sample(trtsdt_int:trtedt_int, size = 1) * 86400), origin = "1970-01-01")
      c4d1_date <- min(c2d1_date + 60 * 86400, pinfo$TRTEDTM)

      tibble::tibble(
        STUDYID = pinfo$STUDYID,
        USUBJID = pinfo$USUBJID,
        PARAMCD = as.factor(c(rep("OVRINV", 6), "BESRSPI", "INVET")),
        PARAM = as.factor(dplyr::recode(
          .data$PARAMCD,
          OVRINV = "Overall Response by Investigator - by visit",
          OVRSPI = "Best Overall Response by Investigator (no confirmation required)",
          BESRSPI = "Best Confirmed Overall Response by Investigator",
          INVET = "Investigator End Of Induction Response"
        )),
        AVALC = c(
          rsp_screen, rsp_bsl, rsp_c2d1, rsp_c4d1, rsp_eoi, rsp_fu,
          names(param_codes)[best_rsp],
          rsp_eoi
        ),
        AVAL = param_codes[.data$AVALC],
        AVISIT = factor(c(avisit, avisit[best_rsp_i], avisit[5]), levels = avisit)
      ) %>%
        merge(
          tibble::tibble(
            AVISIT = avisit,
            ADTM = c(scr_date, bs_date, c2d1_date, c4d1_date, eoi_date, flu_date),
            AVISITN = c(-1, 0, 2, 4, 999, 999),
            TRTSDTM = pinfo$TRTSDTM
          ) %>%
            dplyr::select(-"TRTSDTM"),
          by = "AVISIT"
        )
    }) %>%
    Reduce(rbind, .) %>%
    dplyr::mutate(
      AVALC = factor(.data$AVALC, levels = names(param_codes)),
      DTHFL = factor(sample(c("Y", "N"), nrow(.), replace = TRUE, prob = c(1, 0.8)))
    )

  adrs <- var_relabel(
    adrs,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge ADSL to be able to add RS date and study day variables
  adrs <- dplyr::inner_join(
    adsl,
    adrs,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  )

  tmc_ex_adrs <- adrs %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$AVISITN,
      .data$ADTM
    )

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adrs")
  formatters::var_labels(tmc_ex_adrs) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adrs)])
  rm(tmp_dt)

  save(tmc_ex_adrs, file = "data/tmc_ex_adrs.rda", compress = "xz")
}

## ADTTE

generate_adtte <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  lookup_tte <- tibble::tribble(
    ~ARM, ~PARAMCD, ~PARAM, ~LAMBDA, ~CNSR_P,
    "ARM A", "OS", "Overall Survival", log(2) / 610, 0.4,
    "ARM B", "OS", "Overall Survival", log(2) / 490, 0.3,
    "ARM C", "OS", "Overall Survival", log(2) / 365, 0.2,
    "ARM A", "PFS", "Progression Free Survival", log(2) / 365, 0.4,
    "ARM B", "PFS", "Progression Free Survival", log(2) / 305, 0.3,
    "ARM C", "PFS", "Progression Free Survival", log(2) / 243, 0.2,
    "ARM A", "EFS", "Event Free Survival", log(2) / 365, 0.4,
    "ARM B", "EFS", "Event Free Survival", log(2) / 305, 0.3,
    "ARM C", "EFS", "Event Free Survival", log(2) / 243, 0.2,
    "ARM A", "CRSD", "Duration of Confirmed Response", log(2) / 305, 0.4,
    "ARM B", "CRSD", "Duration of Confirmed Response", log(2) / 243, 0.3,
    "ARM C", "CRSD", "Duration of Confirmed Response", log(2) / 182, 0.2
  )

  evntdescr_sel <- c(
    "Death",
    "Disease Progression",
    "Last Tumor Assessment",
    "Adverse Event",
    "Last Date Known To Be Alive"
  )

  cnsdtdscr_sel <- c(
    "Preferred Term",
    "Clinical Cut Off",
    "Completion or Discontinuation",
    "End of AE Reporting Period"
  )

  adtte <- split(adsl, adsl$USUBJID) %>%
    lapply(FUN = function(pinfo) {
      lookup_tte %>%
        dplyr::filter(.data$ARM == as.character(pinfo$ACTARMCD)) %>%
        dplyr::rowwise() %>%
        dplyr::mutate(
          STUDYID = pinfo$STUDYID,
          USUBJID = pinfo$USUBJID,
          CNSR = sample(c(0, 1), 1, prob = c(1 - .data$CNSR_P, .data$CNSR_P)),
          AVAL = stats::rexp(1, .data$LAMBDA),
          AVALU = "DAYS",
          EVNTDESC = if (.data$CNSR == 1) {
            sample(evntdescr_sel[-c(1:2)], 1)
          } else {
            ifelse(.data$PARAMCD == "OS",
              sample(evntdescr_sel[1], 1),
              sample(evntdescr_sel[c(1:2)], 1)
            )
          }
        ) %>%
        dplyr::select(-"LAMBDA", -"CNSR_P")
    }) %>%
    Reduce(rbind, .)

  adtte <- var_relabel(
    adtte,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge ADSL to be able to add TTE date and study day variables
  adtte <- dplyr::inner_join(
    adsl,
    dplyr::select(adtte, -"ARM"),
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(TRTEDTM)),
      is.na(TRTEDTM) ~ floor(trtsdt_int + (study_duration_secs) / 86400)
    )) %>%
    dplyr::mutate(ADTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ADTM)

  adtte <- adtte %>%
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(PARAM = as.factor(.data$PARAM)) %>%
    dplyr::mutate(PARAMCD = as.factor(.data$PARAMCD)) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$ADTM
    )

  # adding adverse event counts and log follow-up time
  tmc_ex_adtte <- dplyr::bind_rows(
    adtte,
    data.frame(adtte %>%
      dplyr::group_by(.data$USUBJID) %>%
      dplyr::slice_head(n = 1) %>%
      dplyr::mutate(
        PARAMCD = "TNE",
        PARAM = "Total Number of Exacerbations",
        AVAL = stats::rpois(1, 3),
        AVALU = "COUNT",
        lgTMATRSK = log(stats::rexp(1, rate = 3)),
        dplyr::across(c("ADTM", "EVNTDESC"), ~NA)
      ))
  ) %>%
    dplyr::arrange(
      .data$STUDYID,
      .data$USUBJID,
      .data$PARAMCD,
      .data$ADTM
    )

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adtte")
  formatters::var_labels(tmc_ex_adtte) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adtte)])
  rm(tmp_dt)

  save(tmc_ex_adtte, file = "data/tmc_ex_adtte.rda", compress = "xz")
}

## ADCM

generate_adcm <- function(adsl = tmc_ex_adsl) {
  set.seed(1)
  max_n_cms <- 10L

  lookup_cm <- tibble::tribble(
    ~CMCLAS, ~CMDECOD, ~ATIREL,
    "medcl A", "medname A_1/3", "PRIOR",
    "medcl A", "medname A_2/3", "CONCOMITANT",
    "medcl A", "medname A_3/3", "CONCOMITANT",
    "medcl B", "medname B_1/4", "CONCOMITANT",
    "medcl B", "medname B_2/4", "PRIOR",
    "medcl B", "medname B_3/4", "PRIOR",
    "medcl B", "medname B_4/4", "CONCOMITANT",
    "medcl C", "medname C_1/2", "CONCOMITANT",
    "medcl C", "medname C_2/2", "CONCOMITANT"
  )

  adcm <- Map(function(id, sid) { # nolint
    n_cms <- sample(c(0, seq_len(max_n_cms)), 1)
    i <- sample(seq_len(nrow(lookup_cm)), n_cms, TRUE)
    dplyr::mutate(
      lookup_cm[i, ],
      USUBJID = id,
      STUDYID = sid
    )
  }, adsl$USUBJID, adsl$STUDYID) %>%
    Reduce(rbind, .) %>%
    `[`(c(4, 5, 1, 2, 3)) %>%
    dplyr::mutate(CMCAT = .data$CMCLAS)

  adcm <- var_relabel( # nolint
    adcm,
    STUDYID = "Study Identifier",
    USUBJID = "Unique Subject Identifier"
  )

  # merge adsl to be able to add CM date and study day variables
  adcm <- dplyr::inner_join( # nolint
    adcm,
    adsl,
    by = c("STUDYID", "USUBJID"),
    multiple = "all"
  ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(trtsdt_int = as.numeric(as.Date(.data$TRTSDTM))) %>%
    dplyr::mutate(trtedt_int = dplyr::case_when(
      !is.na(TRTEDTM) ~ as.numeric(as.Date(.data$TRTEDTM)),
      is.na(TRTEDTM) ~ floor(.data$trtsdt_int + (.data$study_duration_secs) / 86400)
    )) %>%
    dplyr::mutate(ASTDTM = as.POSIXct(
      (sample(.data$trtsdt_int:.data$trtedt_int, size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(astdt_int = as.numeric(as.Date(.data$ASTDTM))) %>%
    dplyr::mutate(ASTDY = ceiling(as.numeric(difftime(.data$ASTDTM, .data$TRTSDTM, units = "days")))) %>%
    # add 1 to end of range incase both values passed to sample() are the same
    dplyr::mutate(AENDTM = as.POSIXct(
      (
        sample(.data$astdt_int:(.data$trtedt_int + 1), size = 1) * 86400),
      origin = "1970-01-01"
    )) %>%
    dplyr::mutate(AENDY = ceiling(as.numeric(difftime(.data$AENDTM, .data$TRTSDTM, units = "days")))) %>%
    dplyr::select(-"trtsdt_int", -"trtedt_int", -"astdt_int") %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM)

  tmc_ex_adcm <- adcm %>% # nolint
    dplyr::group_by(.data$USUBJID) %>%
    dplyr::mutate(CMSEQ = seq_len(dplyr::n())) %>%
    dplyr::mutate(ASEQ = .data$CMSEQ) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(.data$STUDYID, .data$USUBJID, .data$ASTDTM, .data$CMSEQ) %>%
    dplyr::mutate(
      ATC1 = paste("ATCCLAS1", substr(.data$CMDECOD, 9, 9)),
      ATC2 = paste("ATCCLAS2", substr(.data$CMDECOD, 9, 9)),
      ATC3 = paste("ATCCLAS3", substr(.data$CMDECOD, 9, 9)),
      ATC4 = paste("ATCCLAS4", substr(.data$CMDECOD, 9, 9))
    ) %>%
    dplyr::mutate(CMINDC = sample(c(
      "Nausea", "Hypertension", "Urticaria", "Fever",
      "Asthma", "Infection", "Diabete", "Diarrhea", "Pneumonia"
    ), dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMDOSE = sample(1:99, dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMTRT = substr(.data$CMDECOD, 9, 13)) %>%
    dplyr::mutate(CMDOSU = sample(c(
      "ug/mL", "ug/kg/day", "%", "uL", "DROP",
      "umol/L", "mg", "mg/breath", "ug"
    ), dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMROUTE = sample(c(
      "INTRAVENOUS", "ORAL", "NASAL",
      "INTRAMUSCULAR", "SUBCUTANEOUS", "INHALED", "RECTAL", "UNKNOWN"
    ), dplyr::n(), replace = TRUE)) %>%
    dplyr::mutate(CMDOSFRQ = sample(c(
      "Q4W", "QN", "Q4H", "UNKNOWN", "TWICE",
      "Q4H", "QD", "TID", "4 TIMES PER MONTH"
    ), dplyr::n(), replace = TRUE))

  # Adding labels
  tmp_dt <- scda::synthetic_cdisc_dataset("latest", "adcm")
  formatters::var_labels(tmc_ex_adcm) <- as.character(formatters::var_labels(tmp_dt)[names(tmc_ex_adcm)])
  rm(tmp_dt)

  save(tmc_ex_adcm, file = "data/tmc_ex_adcm.rda", compress = "xz")
}
```

## Generate Data

```{r generate data, eval=FALSE}
# Generate & load adsl
tmp_fol <- getwd()
setwd(dirname(tmp_fol))
generate_adsl()
load("data/tmc_ex_adsl.rda")

# Generate other datasets
generate_adae()
generate_adlb()
generate_adrs()
generate_adtte()
generate_adcm()

setwd(tmp_fol)
```
